Everybody always begins their acknowledgments with the same sentence: “I'd like to thank this person… blah blah blah”. I, however, would like to give my first thanks to Life which is ironic, considering what Life is. It's cruel, it's unfair, it's tragic and overly dramatic for no apparent reason. But what is tragedy without hope? What is darkness without sunshine? There is always, always a Sunshine, always something positive in this world. I am lucky enough to have more than one sunshine in my life.

Audrey. My dear, dear Audrey. There aren't enough words to express how grateful I am that I have met you. There has always been joy in your presence, there was something that clicked. You are the one who understands my crazy ideas that don't make any sort of sense, you are the one that said you liked my stories. That is why I kept writing. You were and are the one who supports my extravagant plans. You are the one that believes in me, my potential, my skills. You are better than a best friend, you are an Audrey. Everybody needs an Audrey in their life.

Hamza. You were so incredibly supportive of this book having read none of it, not even one word. That was always a surprise to me. Even \textit{I} was skeptical about its quality at times, but you kept saying that I'm such a great writer, that I'm gonna be famous some day. You believed in me. And you still do. That's such a weird thing to say: “I believe in you”, but you did. You believe in me with all your soul and I'm so beyond grateful for that. Love you with all my heart.

The most important person I could possibly acknowledge is, of course, Igor. Firstly, because if I don't, he's going to get mad. And we all know you do \textit{not} want to make Igor mad. Alright, all jokes aside though, we do have our differences at times but that's okay. I know you love me with all your heart, and I do, too. I really do. I love you to the moon and back! Thank you for being this excited for my book, thank you for channeling part of that never-ending energy into the impatience of it all, that is so, so incredibly sweet.

And, last but definitely not least, I'd like to acknowledge my family. Family is the most important thing in this world. My parents, all of my grandparents, my great grandma—my relatives—they all shaped me into a decent person and are still doing it to this day. I always learn something new because of them. And that is so unbelievably amazing!

I love all of the people I've mentioned above from the bottom of my heart, I hope they all know that!