“What’s that supposed to mean?” she asked, knitting her eyebrows into a frown.

“Well, you’re a girl…” he said, all his confidence reflected in his expression.

“And you’re a boy. What else is new?” she cut him off, crossing her arms on her chest and taking a few steps farther from him.

He surely didn’t mean what he said and looked like he wanted to apologize. But he decided to keep going because he knew it was the only way to persuade her to do something she would never do. And so he continued on with his rudeness:

“Emily, you are not to deny that girls are scared of literally everything!”

Emily felt disgusted. But she was also in shock because her friend wasn’t normally like this—she knew him well enough to say he wasn’t sexist. But what was up with him? She had no idea.

“No, \textit{Charlie}," she emphasized his name as he did with hers, "that is not true. Girls just happen to not be afraid to show their feelings and are notembarrassed of them!”

“It is true. I can’t show you that I’m afraid,” he replied, narrowing his eyes at her. “Probably because I’m not. Unlike you.”

“What are you talking about? I am definitely not scared to go wandering into the abandoned house of a photographer. You know, the mad photographer whose wife went missing right before he and his son disappeared as well!” Emily retorted sarcastically.

“Alright then. Let’s go!” Charlie exclaimed as he picked up his backpack and headed towards the freshly painted white fence.

The sun was setting and illuminated his dark silhouette as he reached for the gate. The light, warm spring breeze drifted    through his short, untidy ash-brown hair, making it flutter slightly as he smiled and motioned his head toward the road separating Emily’s front yard from the other houses down the street.

Emily sighed and, having known him for over eight years, she knew it would be impossible to convince him that this was a horrid idea, now that he was determined to do it.

“Fine,” she said grumpily and then, slightly cheering up and looking at him with a sort of sly smile, she added, “But tomorrow. After school.”

Charlie rolled his eyes but opened his mouth to agree, when Emily continued:

“If…”

Charlie looked at her disapprovingly.

“\textit{If} you pass tomorrow’s biology test.” Emily was finally confident with her words.

And so Charlie had to agree or else, he thought, he wouldn’t be able to explore the "haunted" house with his best friend.

He nodded reluctantly, lifted his skateboard from its leaning position against the fence, jumped over it instead of opening the gate and set off into the sunset.