Emily left her gym class with a frustrated look on her face.

“Can you believe Jimmy and Jane kept pushing me?!” she was telling a girl with uncontrollably curly red hair that stood out in places it wasn't supposed to.

“Well, Em, you pushed Jimmy first, and Jane was trying to protect herself before you could do the same to her,” the girl replied as they walked up to their lockers.

“Come on, Liz!” Emily groaned, putting her history and science books into her bag, “Jimmy was being unreasonable, I mean, he wasn't giving me the ball! And Jane is…”

“…irritating! I know! But Jim and you were on different teams, gosh!” Liz said with a grin.

“Oh, well, you could have told me that! Do you really think I heard Mr. Grace over all that…?” Emily didn't finish her sentence.

“Hold on. Is that Matthew over by the forty-third locker?” Liz pointed down the corridor, looking excitedly at her best friend, who immediately turned to where the tall, red-haired girl was gesturing.

“What?!” Emily looked back at Liz. “How long has...?”

“He's coming over!” Liz said suddenly.

“There's no way he's coming…”

“Yes, he is!” Liz exclaimed.

“Please help me… uh…” She looked down at herself. “Undo my braids!”

Emily grabbed one of her blonde braids, shoved the other one into her friend's hand and started untying chaotically.

Once that was done, it revealed silky shoulder-length wavy hair, which belonged to the light-skinned but freckled girl with ocean-blue eyes.

“How do I look?” she asked.

“Cool,” said a voice from behind her, which definitely did not belong to the girl standing in front of her.

Turning around, there was no surprise that the deep and raspy voice belonged to a tall boy with light-brown skin, which suited his curly auburn hair nicely.

“M… Matthew,” Emily stuttered then, turning around back to Liz, she saw that her friend was shaking her head comically, disapproval all over her face.

Emily was slightly abashed: she only stuttered when she was nervous. Nevertheless, she went back to the conversation with Matthew:

“I didn't… I didn't see you there. So… what's up?”

The boy smiled and replied, “Oh, not much. How is it going with you?”

“I don't know, I mean… I mean I do know. You get it, right?” she replied, wrinkling her nose and narrowing her eyes.

“Not really, no,” Matthew answered, smiling even more, now showing his healthy white teeth.

“Well…” She searched for a topic.

“I like your… your clothes,” and as she said that, she rubbed the bridge of her nose, embarrassed.

Matthew looked down to see what he was wearing: a red and black checkered shirt, jeans with holes for knees and a pair of muddy red snickers with white stars drawn all over them.

“Thank you?” he said, a bit confused, “That's not really what I came here for. Are you free after school?”

Emily looked at him as if horrified. “ME?! Yes, me… erm, I'm free!”

“Cool. There's a new frozen yogurt store across from school and if you wanted to go…”

“Yes!”

“Alright then, see you after school.” He smirked weirdly and strode off toward one of the classrooms.

Emily turned around yet again to find her friend smiling broadly:

“See, I told you he liked you!”

Emily was on the verge of jumping, happiness overfilled her lungs.

“Well, I don't know about that!”

She tried to act as if nothing happened and it's every day that her crush wanted to talk to her, but she couldn't help it:

“Do you really think Matthew likes me???” she asked Liz, jumping up and down, unable to contain herself. Her friend smiled in reply.

\bigskip

It was lunchtime and after having a tiring computer class, Emily and Liz headed down to the cafeteria.

As they grabbed the trays from the stack at the lunch line and got food practically thrown at them by the busy lunch lady, they were chatting about Matthew and how cool it was that he had asked Emily out.
They had somehow managed to find an empty table in the chaos that was their school's cafeteria and took their seats.

Just then another orange tray was slammed onto their table, followed by a voice half-shouting:

“How could you?!”

It was Charlie. He had sat down next to Liz, staring right into Emily's eyes as he spoke.

“What's… wrong?” Emily questioned hesitantly, puzzled by her friend's sudden outburst.

“We were supposed to explore the house together after school!” he said furiously.

“Well, yeah...”

“And you decided that getting frozen yogurt with Matthew Miller instead was much cooler!”

“What… How do you know about that?!” the blond girl exclaimed.

“I was standing right behind you in the lunch line!”

“Oh… I'm…”

“You promised we'd go. So what's up with that?!”

“Only if you'd pass the biology test!” Emily said, hoping that he didn't manage to.

“Well, I did in fact pass it.” Charlie searched his pockets for a crumpled up piece of paper, spread it open for the girls to see and slammed it on the table. “I got an A-!”

Emily stared uncomfortably at the shiny, bright red letter "A" with a "-" standing beside it, written at the top of the page.

“So what's up with you making plans with someone else when we had an agreement?” Charlie continued, looking angrily at his good grade as if it was the test's fault.

“Well, I… erm,” Emily started.

“Just go with Miller then!” Charlie replied, not letting the blond girl explain herself.

“Now hold on a second! Charlie, I don't think you're being very reasonable. Do you know how long Matthew has been Emily's crush for? And do you know the feeling of…” Liz stepped into their fight but was interrupted.

“Elizabeth Manthey Anderson, I strongly recommend you \textit{not} to meddle in other people's business.” And with those words Charlie got up from the table and started walking toward the cafeteria door, leaving his tray and the biology test.

The girls stared blankly at the piece of paper that was left behind and then, as if waking up from a trance, Liz spoke:

“Rude much! I mean you had wanted to talk to Matthew ever since you were in, like, elementary school! Why can't Charlie understand that?” But she was interrupted.

“No, he's right. I shouldn't have made any plans…” Emily said quietly.

“I should apologize and make sure he's okay,” she added suddenly as she stood up from her seat and ran off after her sad friend.