Emily caught up with Charlie in the hallway packed with lockers and students, all hurrying somewhere, banging their locker doors shut. As she reached him, Emily grabbed Charlie by the shoulder, obligating him to stop walking and turn around.

“What do you want?” he asked rudely, shrugging Emily's hand off of his shoulder, “Come to tell me what kind of toppings you'll have with your frozen yogurt?”

“No! Besides, I didn't gloat about that at all. You're overreacting!” she replied.

“'You're overreacting' is what you wanted me to hear?” he questioned, raising his eyebrow.

“No,” she took a deep breath, “I've come to ask you… Well, you… you aren't having anxiety problems again, are you?”

Emily took Charlie's hand, looking worried.

Charlie didn't look so keen on her asking that. He took a long deep breath that went unnoticed by Emily and turned his head around to see if anybody else heard her question. Luckily, everybody was busy with their own troubles.

“This has \textit{nothing} to do with my 'problems', okay?” he emphasized every word and then added: “Besides, why do you care? Didn't seem so caring back when Miller invited you to get yogurt.”

Emily gave him a sharp look and let go of his hand.

“Well, neither did you care when you called me 'scared' because I am a 'girl',” she stated firmly.

“That is literally the only way to get you to do stuff with me!”

“There is always another way! Without hurting anybody's feelings!”

The blond girl said it in a sort of daring tone, which made Charlie think that her making plans with Matthew was a sort of payback.

“So you're saying this is your 'revenge plan'?” he asked accusingly.

“Yeah, sure,” she replied without hesitating. And then turned around and walked away.

\bigskip

“Are you telling me that THIS," Liz asked, holding up a sweatshirt from the pile of clothes on the bed, "is your 'revenge plan' against Charlie?”

It was sunny outside. The gentle breeze carried the crystal fresh air into Emily's bedroom through the open window. The lavender and white room was nice and clean with a canopy bed, plenty of wardrobes and cabinets, a big circular mirror with yellow smiley faces hand-painted by Emily herself, lots of posters and a huge bookshelf piled with loads of books. The only mess was now lying on her bed.

“No! I've already told you! I'm just teaching him a lesson. That's all… Then I'll go with him to his stupid ghost house,” Emily told Elizabeth again for the fourth time. “Did you come here to interrogate me?”

“No, I've come here to help you pick out an outfit for your first date!” Liz told her excitedly.

“I don't \textit{need} an outfit.”

“Then why did you let me dump out half your closet onto your bed?”

“Look, just pick anything you want if it means so much to you!” Emily replied, getting frustrated.

“Hmm, let's see… Wait, aren't you supposed to be there right after school?” The red-haired girl stopped before picking up a dark-blue leather jacket from the pile.

“Yes, but Matthew has two lessons more so I have plenty of time…” she replied and then, looking at the watch on her wrist, suddenly stood up from the floor she was sitting on.

“I'm late!” Emily informed.

“I still haven't picked out your outfit…”

“I hate being late so pick faster!”

While Liz began to fumble around through the pile, Emily was anxiously pacing up and down the room.

And then the redhead produced a smaller pile of clothes from the one on the bed and was about to hand it over to Emily when the doorbell rang.