“I don't have time for this. Liz! How \textit{long} does it take to get to that frozen yogurt place?” Emily shouted, heading towards the front door.

“At least…” her friend began to say but couldn't be heard over the rush of thoughts in Emily's head when she opened the door and found her other best friend, Charlie, on the doorstep.

“What are you doing here?” she asked crossly.

“I came to apologize…” Charlie answered awkwardly.

He shuffled his feet on the doorstep. Emily was beyond glad that he didn't use his key but rang the doorbell instead.

“I'm sorry. I was wrong to call you 'scared' merely for your gender, and I'm hoping you'll accept my apology and we can finally go to the 'stupid ghost house'?” he smiled, being proud for choosing the right words for once.

“What?!” She seemed startled. “How do you know about the 'stupid ghost house'?!”

“Well, that's what you're probably thinking it is, right?”

“Yeah, um, totally.” For a moment Emily thought that Charlie somehow eavesdropped on her conversation with Elizabeth. “And I… erm, accept your apology and I'm also deeply sorry for hurting your feelings as well…”

Charlie was on the verge of hugging Emily, but just then Liz came down to the front door.

“Aren't you supposed to be late? Oh. Hi, Charlie,” she called.

“Late for what?” the boy asked.

Emily, now feeling uncomfortable, took a deep breath and turned to face him:

“Charlie, I'm really terribly sorry, but Matthew and I have already arranged to meet up right after school and, er… I'm sorry, I \textit{do} have to go.”

The ash-brown haired boy didn't look too happy upon hearing this.

“Oh, okay then,” he replied dryly as he had hoped that his apology would convince Emily to explore the haunted house with him instead.

Liz, having been standing there the whole time, was now holding out a knitted vest, yellow skirt and a white blouse for Emily.

"Charles! I was thinking...” she started brightly but was interrupted by him muttering, "Was it hard for you?"

Ignoring this remark, Liz continued:

“What if you gave Emily a ride to school on your skateboard? You do have it with you, don't you?”

“Of course he has it!” Emily exclaimed and then, turning to him, smiled hopefully.

“One word: no,” Charlie answered quickly, scowling.

“Oh, please? We can go to the house right after!”

“You mean today?”

“Well, no, not today but first thing after school tomorrow.”

“Isn't 'right after' supposed to actually \textit{mean} 'right after'?” Charlie questioned reproachfully.

“Oh, come on. Em's already late!” Liz stated crossly, “We don't have time for your usual behavior, Charlie.”

“What is that supposed to mean?!” Charlie crossed his arms on his chest.

“Yes or no to dropping me off?” Emily asked so fiercely that Charlie decided it was best to not argue with her any further.

“Alright, I'll drop you off but don't…”

“Yeah, yeah, blah, blah, blah,” Liz rolled her eyes, shoving the clothes into Emily's hands and pushing her down the corridor to her room.

Then, turning to the scowling boy, she started:

“You do have a spare helmet, right? Because riding a skateboard requires you to wear one…”

“I know that, thank you \textit{very} much,” Charlie interrupted, annoyed.

The moment Emily came out of her bedroom wearing her "date outfit", Elizabeth pushed her and Charlie out of the house, following right behind them.

“We better get going,” Charlie stated dryly, shoving a protective helmet into his best friend's hands.

“Wait, isn't this your helmet? Do you have a spare?” Emily asked curiously.

“No questions, please. Just put it on!” Charlie exclaimed, knowing perfectly well he didn't have a spare one but wanting Emily to be safe.