Even though Emily saw Charlie take off, she really did not. Charlie returned two minutes after she went inside, making a circle around the block. He crept around from behind the building and squeezed in between the rose bushes and the big glass windows, leaving thorn cuts on his arms and legs. The ash-brown haired boy then crouched down so that he could get a clear view of a couple of other people’s legs and, most importantly, Emily and Matthew.

He sat there for a couple of hours, attracting some questionable looks from passersby.

“Wow, Matthew is so dull,” Charlie muttered under his breath, as not one single time did Emily laugh during their conversation.

But just then, she smiled widely at Matthew, making him smile back at her.

“\textit{Now} what is she smiling about?!” Charlie exclaimed anxiously.

Matthew then began to lean in towards Emily, which made Charlie’s eyes pop out.

He stood up and, tearing a piece of his T-shirt on the thorns of the bushes, ran up to the entrance and dashed inside. He made his way up to the table where Matthew now sat in his normal position with a napkin in his hands. Observing their seating arrangement, Charlie noticed that the napkins were lying on Emily’s side.

Emily turned her head to the towering figure over their table and, as she spoke, her voice was full of shock.

“What are you doing here?” she questioned.

“Huh?” Charlie replied.

“What are you doing here?” she repeated herself more clearly, emphasizing every word.

“I,” he began, as he scanned the inside of the building, looking for excuses, “I… am… here… because… I saw the… the news!”

“Okay, but that doesn’t explain why you are here,” Matthew pointed out.

“No one asked \textit{you} to speak!” Charlie exclaimed angrily, “But for your information, I am here because the man in the news told me that… this place was on fire! So I ran here… and… it’s not on fire, so I’m glad you’re alright. Okay, bye.”

“Do you mean the news on the TV over there with the woman?” Emily asked in a sarcastic tone, pointing to the TV high up on a wall, broadcasting the daily news.

“No!” Charlie replied in his nervous, squeaky voice and then, clearing his throat, spoke in his normal one: “There are other news channels, with a… man! Okay, well, I’m glad you’re fine, so Emily and I will be taking off now.”

“Erm, no, thank you. I think I’ll stay here for a while…” Emily began but was cut off by her best friend.

“Alright, come on!” he said, as he took her by the elbow and led her outside.

The now fresh but warm evening breeze swept their hair as they stepped out onto the pavement and Charlie let go of her.

“Now, what was that all about?” Emily whispered angrily.

“I thought you were finished, and since I'm here, I might as well give you a ride to your house,” he shrugged.

“No! No, I wasn’t ‘finished’! No!” she answered furiously.

“Well, looks like Miller has,” Charlie pointed behind Emily to where Matthew was coming out of the frozen yogurt store.

“If you hadn’t dragged me away he wouldn’t be ‘finished’,” Emily retorted.

Just then Matthew came over to the two and addressed Emily:

“Hey! If you’re going home, I can walk you to your house,” and, lowering his voice, added: “But I’d drop the crazy news guy…”

Emily smiled and followed Matthew, leaving Charlie alone on the street.