The day after the "silly little incident"—that's what Charlie called the whole "date thing" in his head—was one of the worst days for him yet. He was being avoided by his best friend the whole time he was at school, even during lunch. But when classes ended, he finally caught her by the lockers.

“Hi!” he said brightly, pretending nothing had happened.

She glanced at him but went back to unloading her backpack, not even letting out so much as a scoff. Charlie's expression changed quickly: he knew he had to apologize. Though, he was probably right, he thought, and it was mostly the \textit{way} he had acted that bothered Emily. Maybe if he had asked her not to go on the date, she would have listened because… well, because Matthew merely can't be trusted. Charlie does know what's best for Emily and he definitely knew that she deserves better…

But meanwhile, in the real world and not in Charlie's mind, Emily was still not speaking with him and was about to leave. That's when Charlie decided to finally talk:

“Um, sorry about yesterday… I guess I was having anxiety problems or something… I don't know why I bursted in on you like that…”

“Are you trying to make me forgive you by feeling sorry for you?” Emily questioned, irritated by the fact that this might be true.

“No, of course not,” Charlie replied, “I'd never do that! So… are we good?”

Emily kept silent.

“Okay, well… we are going to the haunted house today, right?” he continued and, before Emily could interrupt him, added, “You wouldn't break a promise, would you?”

“Fine. I guess we are still going to that place after school,” Emily rolled her eyes.

“Good.”

\bigskip

“So, are you ready to explore this place?” Charlie asked, excitement in the air.

He had dragged Emily all the way to the outskirts of town and she, on the other hand, wasn't excited at all. There weren't many houses, thus not many people, making it look like the whole area was abandoned and not just the old, dilapidated house they were standing in front of.

“You know, I don't think we have to actually go in. I mean we can admire the house from here!” she said, trying not to sound intimidated by it.

“'Admire'?! Are we art critics now?” Charlie answered and, knowing she'd probably bail out, proceeded on to making chicken sounds.

“Wh… What are you doing?” she questioned, thoroughly confused.

“Is \textit{the} Emily Parker actually chickening out?” he asked mockingly, continuing on with embarrassing himself by clucking even louder.

“Oh, cut it out, will you,” she sighed, rolling her eyes and, when he calmed down, continued, “What I meant to say was that we are not prepared for this 'adventure'.”

“Ohhh, I get it! You need to stop being a chicken before you can actually enter the house! Very smart move indeed.”

“No. What I mean is we don't have any water or food with us… and, and… no flashlights, rope… We don't have any anything!”

The chicken sounds finally stopped and Charlie looked at the blond girl disapprovingly.

“Oh, come on! Why are you always paranoid?” he exclaimed.

“\textit{I'm} paranoid?!”

“Yes!”

“What about you?!”

“Me?”

“Yeah! You never ride your skateboard without a helmet even though you and I perfectly know that you're not gonna fall off!” she said.

“That's not true! I don't need it anymore!”

Emily gave the ash-brown haired boy a reproachful look. He looked down at his sneakers.

“Alright, you've got a point,” he mumbled finally and then quickly added, “About the house I mean.”

“And I think it's best if we go during the weekend so that if something happens we won't miss out on school.”

“Okay, yeah yeah yeah, fine, let's just go home…” Charlie replied, unsatisfied.

He bent over to pick up the skateboard which he had brought with him and then got up sharply, leaving it there, and was preparing to run. All because he had a weird tingly sense that something was going to happen. And that sense was right.

There was a loud crash.

It was followed by a "THUD".

And it all came from the side of the rode.

Then the two friends, already frightened as hell, heard the rustling of the nearby bushes.

Charlie volunteered to show that he was not a scaredy cat and slowly walked over to the bush with Emily close by him, all the while thinking that this is exactly how characters in horror movies die.

He reached his hand out reluctantly, took a deep breath and moved the branches of the bushes apart.

Nothing.

“Huh,” Charlie breathed out, grateful that no killer with a chainsaw and a mask had jumped out at them.

“Yeah, strange…” Emily agreed.

“Oh, look!” He pointed to a trashcan standing very close to the rustling bush in question. “It's probably a raccoon or something. Nothing dangerous…”

“Yeah, probably…” she replied, relief filling her lungs.