The black cat lay still on the grass, the sunlight reflecting off her silky fur. She lay in peace, enjoying the moment, squinting at the yellow ball of fire in the sky when a fairly large ginger tomcat was planted beside her by an annoying ash-brown haired boy. The ginger cat began prancing around her, trying to catch her attention, but she merely ignored him. The tomcat was getting annoyed by the fact that his owner was getting along just fine with the beautiful black cat’s owner whilst he, Jasper, couldn’t even make the female cat look at him. Jasper decided it was best to jump onto the black cat so she would like him, which he did. In one elegant motion, he plunged into the air and, with the same elegance, landed onto the black cat’s back.

Although Jasper’s intentions were good, the black cat did \textit{not} enjoy it at all, which was very strange to him. She hissed and, with the upmost disgruntled look on her face, ran from him and took cover on the blond girl’s lap.

“Charlie! Your cat is jumping on Angela again!” Emily exclaimed angrily as she comforted her beloved pet.

“Oh, come on, he just wants to play with her, and she keeps ignoring him!” Charlie answered, retrieving Jasper to his lap.

“Really? We had to go to the vet because she was traumatized when Jasper wanted to ‘play’ with her!”

“Alright, alright, he won’t bother you…”

For a few minutes, they sat on the soft, tickling grass, cuddling their feline pets. The sun was pouring onto them, making Emily’s freckles stand out even more. It was all quiet except for the buzzing of a lawn mower from next door. That was Charlie’s neighbor.

Emily looked over in the direction of the coming sound and quickly looked back at her friend.

“Charlie…” Emily whispered, “I think we should go inside…”

“Why?” he asked, stroking his cat’s thick fur.

“Um, your neighbor is looking at us again… Maybe even eavesdropping,” she lowered her voice even more.

Charlie merely stood up, jerked his head towards the front door and picked Jasper up, cradling him like a football. The buzz of the lawn mower seemed to die down as Emily followed him. They had just reached the front door when they heard a low and raspy voice behind them say:

“And what are young Miss Parker and Mister Rodriguez up to this time?”

Emily started as they turned around and encountered Charlie’s neighbor standing right behind the fence that separated their houses.

“Nothing, Mister Brown,” they chimed in unison and, as they turned back around and reached for the door handle, they heard the same voice, dragging every word as it spoke, from behind:

“Oh no, I know you two rascals. You two are like chipmunks with their cheeks full of the food they have stolen from my kitchen!” He was shouting the last few words and waving his fist in the air.

Then he turned to face his house and continued:

“I will catch you one day, mister Ticklish! You will not get away with your mischievous plans!”

Emily and Charlie stared blankly at him.

“What does that even mean?” Charlie questioned.

Mister Brown turned back to face them:

“I think I made my point. If I catch you two making one of your silly little plans…”

He then blinked a few times and went back to his house, leaving the unfinished sentence hanging in the air. Charlie quickly opened the front door, let Emily and himself in and closed it behind them.

“So, let’s talk haunted houses,” he smiled brightly.