“I mean, he has been obsessed with this haunted house of his, and he won’t tell me what the big deal about it is.” Emily was poking her Brussel sprouts with the cheap plastic cafeteria fork.

“Emily!” Liz shouted all of a sudden.

“What?!”

“Do you realize that you have been talking about a HOUSE for the past fifteen minutes?”

“Oh, sorry… What were you saying?”

“She was saying that you and I are five minutes late for Bio.” A tall boy was standing beside Liz.

“Um, hi, Matthew,” Emily said nervously, “Sorry, I was just…”

“You can tell me about it on the way if you wanna,” he cut her off, gesturing for her to follow him out of the cafeteria through the nearest set of double doors.

\bigskip

“I just don’t know whether I should go with him or if he just needs someone to talk to,” she finished her story as they entered the classroom.

“If I were you, I’d definitely go…” he trailed off.

“But…?”

“But I wouldn’t want to let you go on your own.”

“Why not?” the girl questioned, smiling.

“It’s far too dangerous.”

“Oh, so you really like me?” Emily said teasingly, her smile so big.

He merely scratched the back of his head awkwardly and went to sit at his desk, leaving Emily to her thoughts.

During biology, whilst the teacher was giving a boring lecture about the digestive system, Emily decided to do something that she thought would cheer Charlie up.

\bigskip

“You want me to go to the haunted house with you and the Rodriguez guy?” Matthew asked, exhilarated, as Emily plopped down beside him at his desk when class had ended.

“Yeah, I mean, why not? Charlie would be thrilled. He thinks your skateboarding skills are breathtaking,” Emily answered in a dreamy sort of way.

“Rodriguez used the word ‘breathtaking’?” Matthew questioned, even more astonished.

“No, I did.”

When the couple caught up with the ash-brown haired boy after school, he did not seem "thrilled" as Emily had anticipated.

“Charlie, don’t be rude please…” Emily said, looking from Charlie who was giving Matthew a death glare to Matthew who was wearing a serene expression on his face.

“I’m not being rude. I just think you’d want to run this by me first, before you go and invite somebody to tag along,” he answered crossly.

“Sorry man, if I’m causing any kind of trouble, I’ll just head home. Alone,” Matthew said apologetically, shrugging.

Charlie rolled his eyes at the boy’s attempt to pity him into agreeing to this. Emily gave him an "I saw that" look. Charlie rolled his eyes again while Emily was trying to convince Matthew that he wouldn’t be third-wheeling.

“Are you sure you’d want me on this adventure of yours?” Matthew kept arguing, “Your friend doesn’t seem to like the idea.”

“Oh, of course we’d want you to come! Right, Charlie?” Emily looked at him sharply, emphasizing his name.

“Uh-huh,” he replied through gritted teeth.

“Fine, I’ll come,” Matthew sighed and then, turning to Emily, said, “Do you want me to walk you home?”

She nodded and, before strutting away with the auburn-haired boy, turned her attention to her best friend, whom she was leaving behind.

“Alright, so we’re all going to the house on Friday after school. It’s settled,” Emily said before smiling and walking off with Matthew.

“Awesome,” Charlie mumbled, pursing his lips.