The sun started to rise. Its rays slipped through the blinds of the one window in the neatly organized lavender and white room. The thin slits of sunlight glided on the blond girl’s freckled face, trying to wake her up but failing to do so. It was one of those calm late spring mornings with the birds’ chirping being heard through the closed window.

Everything was still and perfect. But the world never stays perfect for more than a few seconds.

A loud ringing sound came twice from somewhere beyond the tranquil air of the room. The blond girl shifted around in her canopy bed, squinting her eyes into the morning sunlight streaming through her window. Then, realizing that the sound was not her alarm, she slowly took the warm and welcoming blanket off of her body and stood up as the irritating ringing sound came from the hallway for the third time.

“Who in the burning world of hell goes ringing somebody’s doorbell at this hour?!” Emily muttered under her breath while she hurried along the corridor leading from her bedroom to the front door. Once she saw who was on the doorstep she felt even more tired than before.

“Charlie, what the hell?” she asked, exasperated.

“Good morning to you, too,” he said kindly.

“You know perfectly well that I’m not a morning person!”

“Well, neither am I, but here we both are.”

“It’s five in the morning, what are you doing here?” Emily questioned him through gritted teeth.

Charlie stuttered. He didn’t exactly know what he was doing here, in front of the Parker residence, four hours before school even started. Emily crossed her arms on her chest and leaned against the door frame.

Not being able to come up with a reason for his unexpected visit, he merely stood there in utter silence.

Emily sighed, tilting her head to look at her slippers and stepped over the threshold, closing the door behind her. She didn’t know what was going on with Charlie and, as she looked him straight in the eyes, she felt a stronger wave of concern for him rush through her body.

“Did you even get any sleep?” she asked.

He looked at her, blinking a few times, and then turned around so as not to show his tired eyes.

“Charlie, answer me.” Emily moved to face him.

“No,” he said, swinging his arms awkwardly and trying to avoid eye contact, “I didn’t sleep.”

“Charlie, what’s going on with you?” she questioned, her voice absorbing every drop of distress from her body, “Apparently, you didn't sleep at all last night You’ve been anxious for a long time, haven’t you?”

He mumbled something inaudible in reply, looking down at his sneakers, which were all dirty from the moist grass.

“Is this because of the exams? Because of having to pick a college? Because of your future?” she listed all of the possible roots for his anxiety that she was aware of.

“No, it’s not because of any of that.”

“Then what is it?”

Charlie looked at her for a long time. His Adam’s apple went up and down once or twice. The fresh morning breeze got tangled in his hair. He looked out into the distance, sighed and turned back to Emily:

“Okay, sure. It’s because of all that, but I don’t want to talk about it.”

Emily nodded. She understood his worries even if she didn't get why he felt that way. Understanding the reason behind people’s feelings is very rare because none of us feel everything the same way, but just being able to recognize those feelings means being supportive and sympathetic.

They were now standing there in silence, surrounded by the sound of spring awakening from the night. Neither of them liked sunrises, though. They preferred sunsets and nighttime itself. But even with their dislike for nature’s morning ritual, they stood there, mesmerized.

The pure silence got mixed in with the wind and birds’ songs, and it was the perfect atmosphere for Emily to ask her friend the burning question.

“Why is it scary for you?” she said quietly.

“I don’t know. All I know is it is,” he answered reluctantly. “And very.”

“I know I’ve said this before but… did you try telling your family or, maybe, your teachers?” she asked carefully.

“Like they’d understand…” Charlie snorted in reply.

“Does anybody understand you?”

“Only you a little.” He looked at her again.

“Do you…” Emily asked, “maybe want to study together?”

Charlie didn’t answer. Studying didn’t help, but maybe his mistake was that he was doing it alone.

“Sure,” he exhaled, “But do you mean now?”

“Yeah… no,” Emily said, “Tomorrow maybe? Your house, after school.”

Charlie nodded as Emily headed back to the doorstep. The front door closed, leaving him alone with the morning nature.