“So, are we going to the frozen yogurt place?” Matthew questioned, as Emily joined him at his locker after school.

“Um… I'm sorry but I already made plans with Charlie…” she said uncomfortably.

His expression didn't change. It was the same ‘cool' one that Emily really liked.

“Okay, sure, no problem, so I'll see you tomorrow?” he asked.

“We can still hang out today,” she replied.

“It's okay, we'll see each other tomorrow,” he repeated himself, then gave her a weird smile as he turned around and headed for the exit.

\bigskip

“What are you doing here?” Emily asked Charlie.

She had just arrived at his house but, expecting him to be waiting for her in his bedroom, she found him playing in the yard with his big ginger cat, Jasper.

“Just, you know…” he answered, not wanting to take his eyes of his beloved feline pet.

“Where are all your books?” she asked, as she sat beside him.

“You sound just like my mom,” he said, looking up and squinting at the sunlight.

Emily rolled her eyes and shook her head.

It was five in the evening but the sun wasn't thinking of setting. Its purpose was to blind them but they didn't look up at it a lot.

“Well, how are we supposed to study with no books?” she questioned him.

“Don't you have any books on you?” he asked.

“Well, not exactly…”

“Hey! I thought we were gonna study together!”

“So did I,” she said crossly, “One of us is bound to have the books. And since it's your house, you are the ‘one of us'.”

Charlie lay down on the grass and arched his head so that he could see the Rodriguez residence upside down. He then reached his hands into the sky, plopped them down beside him, looked back at Emily and said in a lazy sort of tone:

“My bedroom's too far.”

“Come on, be serious,” the blond girl answered.

He sat up again and looked back at the house.

“Fine, but you stay right here,” he finally said, “Don't move!”

\bigskip

When he got back with a huge pile of books, he plopped them down right beside his cat, who got so scared of the loud ‘THUD', that he jumped right into Emily's lap.

“What, did you bring your entire library with you?” Emily asked him, as she stroked the poor creature's head.

“You can pick whatever you want,” he said lazily and lay down on the grass again.

“I'm helping YOU, you could've picked at your house!”

“Fine,” Charlie snorted.

Then, not even sitting up, he reached his hand to the pile and took the top book.

“Entry one, I want you to know but I'm not telling,” Charlie read, not paying attention to what he was reading.

“Entry two, at least as deep as the Pacific Ocean, I wanna be yours – Arctic Monkeys,” he kept reading lazily.

“Wait, is this literature or geography?” Emily asked, rummaging in her bag.

“Entry three, she is like being bathed in sunlight – Andrew Garfield,” it seemed like Charlie wasn't even understanding what he was reading.

“Is this social studies?” Emily kept flipping through her textbooks.

“Entry four, what if we think about…” Charlie slowed down, “each other… at the same… time…”

He suddenly became very red in the face, his eyes widened to the size of ping-pong balls and he sat up very quickly.

“Charlie! What book is it? I can't find it!” she said without taking her eyes of her own textbooks.

“Charlie?” she finally looked up at his frozen self, “What book is this?”

She reached her hand to the book which Charlie was still holding wide open in his hands. He immediately closed it shut right before Emily could see it. She was taken aback by this and was wearing a confused expression on her face.

“Sorry, wrong… book…” he said, shifting his gaze.

He threw it to the opposite side of the yard when Emily turned to organize her textbooks into a neat pile. Jasper walked calmly towards the thrown book to sniff it.

“Where did the book go?” Emily asked as she turned back to face her friend.

“It's… uhhhh… it's…” Charlie sighed, not being able to come up with an excuse, “It's there.”

He pointed the way he threw his book with his eyes closed. Emily quickly stood up. When Charlie opened his eyes he immediately realized he needed to stand up too.

As his neighbor approached them, wearing his usual dark beige bath robe, the breeze kept getting entangled in his white hair. He was carrying something rectangular and Charlie's cat seemed to be walking by him, rubbing against his leg. As Emily and Charlie backed away, Mr. Brown came up to them.

“I'm guessing this is yours,” Mr. Brown handed Charlie his special book.

“Thank… you?” Charlie said, confused.

Jasper kept purring and rubbing his face against Mr Brown's ankle fiercely, occasionally looking up at his bemused owner. The neighbor leaned forward to look Charlie right in his face, coming in so close that there was barely enough air in the space between them.

“Now, listen to me,” Mr. Brown said in a serious tone, lowering his voice, as Charlie's eyes widened to the size of ping-pong balls for the second time in the last five minutes, “You and I both know that this ‘Entry fifty six, my last thought will be of you, I promise' stuff is ridiculous…”

“You read my… my journal?!” Charlie exclaimed, clutching his book.

“Now, now, that's stupid of you to say! I just had to read one entry and listen in on your conversation with the girl over there to get all the information that I need…”

“This is NONE of your business, you DON'T need this information!” Charlie interrupted him angrily as Emily stood behind Mr Brown, looking befuddled.

“No, just listen to me,” the crazy neighbor continued, “You need to find someone else.”

“What do you mean? Emily's perfectly fine, she's a great friend…”

“Yeah, yeah, she is, she is,” Mr. Brown cut in blithely, “You can still be friends with her but only if you find someone else to love or obsess over or whatever it is you're doing.”

“Who are you to decide?” Charlie said, infuriated.

“I'm the person who actually understands… this.”

Mr. Brown looked down sadly then looked back up at Charlie and put his hand on his shoulder. Charlie pushed the tanned, wrinkled hand away rudely and walked over to Emily.

Mr. Brown straightened up, sighed, petted the ginger cat who kept circling around his legs and said:

“Alright, so I've given you some advice…” he started when Emily gave him a questioning look, “I mean, I've given him the book.”

Emily nodded understandingly and the neighbor departed, leaving Jasper with nothing to purr about. Charlie walked over to his huge pile of books, picked them up and walked to his front door, his cat following him.

“Wait, where are you going?” Emily asked.

“This study… thing is over,” Charlie answered dryly.

“Oh, okay…” Emily said, bewildered.

This time the door closed, leaving her to stand outside in the blinding orange sun.