Gym class ended. Sweaty students fled from the open door, their foreheads glistening in the fluorescent lights of the hallway.

“I am telling you!” a blond girl kept exclaiming, “It’s not only Jimmy and Jane this time! Amy and Klaus kept pushing me with their stupid elbows!”

“Every Thursday after PE you come up with a new conspiracy theory,” a crazy haired girl replied, rolling her eyes in a playful way.

Emily and Liz reached their lockers. Like every Thursday after that horrendous class was left behind, Emily packed her history and science books into her bag.

“Gosh, remember when you were excited after PE cause Matthew would also finish his class and you would catch a glimpse of him here…” Liz sighed nostalgically.

“Liz, dear, that was only a week ago,” Emily said skeptically.
“Yeah, I know, right? Time flies so fast…” Liz answered, shaking her head with a smile on her face, “Really wish you would still exclaim at how cute he is standing there and then at how cute he is slamming his locker door and then at how cute he is bumping into a person and how cute he is…”

“Yeah, yeah, I get it,” Emily said, half-laughing, “Why do you care if I say he’s cute?”

“Well cause he kinda is.”

“No kidding, you like him too?” Emily asked, mouth open, as she slammed her locker door.

“Nah, not really my type,” she replied, “Anyway, why is it so surprising if I liked him?”

“Well, to be fair, I thought you didn’t like anyone that way,” Emily said as they walked towards the staircase, “And I guess I still think that?”

“Well, actually… I kinda have someone I guess…” Liz trailed off, scratching her head.

“WHAT? For how long?” Emily jumped up, hitting her friend’s arm playfully.

“Um… about a month…” Liz answered as Emily gasped and hit her arm again.

“You. Are. Kidding. And you didn’t tell me?”

“It never came up.”

“Wow, that’s so… wow,” Emily said, all her words fleeing her, “Who is it?”

“Do you remember Lillian?”

“Uhhh… um… is it that girl with the…” Emily stroked her arm with her finger, tracing odd shapes, trying to explain whatever she was saying, “the colored patches of skin?”

“Yeah, it’s called vitiligo,” Liz explained.

“What about her? Lillian?”

“Well, she’s my girlfriend, sort of, I guess…”

“What do you mean ‘I guess’, you’re not sure?” the blond girl chuckled.

“It’s complicated.”

The red haired girl scratched the back of her head. As they rounded a corner, a silhouette of a girl waving to them appeared at the far end of the hallway, all packed with students going here and there. Once they came closer to the girl, it was clear why she was waving. It was undoubtedly Lillian: you could see her dark skin covered in big, distorted white spots. She was beautiful, her pink waist length hair seemed like it was flowing even though there was no breeze.

“Hello,” Emily said in a teasing way, looking excitedly from her friend to the girl who was just waving at them.

“You told her, didn’t you?” Lillian questioned, smiling and narrowing her eyes at Liz.

“Yeah…” Liz said, clutching her bag, “Is it okay?”

“Yep,” Lillian answered and then, turning to Emily, added: “Hi, I’m Lillian but I’m guessing (she emphasized the word) Liz already told you?”

“Yeah, hey, I’m Emily, I’m…” Emily began but was cut off.

“Okay-so-you-know-each-other-you’re-best-friends-now-yay-but-we-have-to-get-going-sorry,” Liz raced through the words, not stopping once for breath.

She then pushed Emily down the hall while saying that they’ll be late for computer class and waving good-bye to a bewildered Lillian.

“So I guess we’ll see each other soon?” was all that Lillian was able to shout to Emily before they were out of earshot.

“What did you do that for?” Emily asked.

“Shhh, the class has started!” Liz answered as they entered the classroom.

“No it hasn’t, we have like five more minutes…”

“Well…” Liz said hesitantly as she seated herself, “I… I have to read my textbook!”

“Oh, alright…” Emily murmured and went to sit at her own desk.