“Why are you so glum?” Charlie said as he sat down at the same table as Emily.

Computer class has ended for Emily and Liz. The moment they were dismissed Liz ran away somewhere, not looking back or waiting for Emily. Now it was lunchtime and the crazy haired girl was nowhere to be seen.

“Liz's being weird,” Emily replied, her mouth full of spaghetti.

“You have JUST noticed this today?” Charlie asked, smiling.

Emily gave him a reproachful look at which he snorted, shaking his head.

“I mean she's being weird now,” Emily grumbled.

“How's the ‘now' weird different from all the other weirds?”

“Maybe it's because of Lillian,” Emily thought out loud, not listening to him.

“Who's Lillian?”

“Oh, I'm not sure if I'm supposed to tell…”

“Tell me what?”

Just then Emily was tapped on the shoulder by a pink haired girl. Lillian looked as if disoriented. Charlie gazed at her cotton-candy-like strands of hair curiously.

“Emily, have you seen Liz anywhere?” she asked nervously.

“No… You can't find her either?” the blond girl replied.

Lillian shook her head and looked like she wanted to say something so Emily patted the seat next to her. The pink haired girl sat down with her tray of food.

“She was very weird today,” Lillian stated, “when she brought you.”

“Yeah, she didn't even wait for me after our class ended, she just ran away as quickly as she could. And she hates running,” Emily shared.

“What is even going on?” Charlie piped in, befuddled.

“Oh, sorry…” Lillian said, looking perplexed and then, leaning closer to Emily, whispered: “Who is that?”

Emily chuckled as Charlie shoved a spoonful of vegetables into his mouth uncomfortably. The blond girl let them deliberately sit there, in silence, the cafeteria noises filling their ears, before speaking:

“That's Charlie, he's friends with me and Liz.”

“Ohhh, you're THAT Charlie! I'm Lillian, Liz's girlfriend,” the pink haired girl stated.

“I'm sorry, Liz's what?” Charlie leaned forward, blinking very fast.

“G-i-r-l-f-r-i-e-n-d,” Lillian spelled out.

Since Charlie sat opposite the two girls, Lillian hadn't noticed the disapproving look Emily gave him. He hesitated, not knowing what to say but after Emily kicked his shin under the table he got his thoughts straight:

“That's awesome, I didn't know Liz was…” he hesitated again.

“A lesbian?” Lillian asked.

“Yeah.”

“She's not. I am.”

“Then what…?” he started.

“She's bi. Surely she told you?”

Lillian looked over at Emily who was shaking her head and then turned back to Charlie and looked at him tentatively.

“Sorry,” he shook his head, then smiled, “No, she did not say ‘Greetings, fellow companions, I'm having turkey for lunch and, by the way, I'm bisexual'.”

The two girls snorted. Charlie did know how to make things un-uncomfortable again with a joke. Though sometimes his jokes were more disturbing than funny…  But still.

Just then Lillian cried out:

“Liz! Over here!”

And turning around, Charlie could see the crazy haired girl slowly heading towards their table. Once she reached them, she didn't sit next to Charlie or put her tray of food down. She looked scared for some reason.

“You okay?” Charlie questioned.

“Yes,” she snapped, “Why does everybody keeping asking me that?”

“Maybe because you answer people this way?” Charlie asked rhetorically.

“What way?” she said, almost through gritted teeth, which shut Charlie up.

“Liz, what's going on?” Emily questioned, looking sideways at Lillian.

“Nothing!” she sighed, exasperated, “Can we please change the subject?”

“Alright,” Lillian nodded kindly.

The three of them sat there in silence, each trying to search for a new topic. Liz stood beside Charlie, tapping her foot. Then she slowly sat on the chair, putting her tray down with her. And just then the boy with the ash brown hair found something to say, breaking the uncomfortable silence:

“Oh, hey! I know about you and Lillian dating! It's great, isn't it?” he looked sideways at Emily who gave him an approving nod.

“Yeah, great,” Liz said and then, suddenly standing up, added: “Excuse me, I have to go.”

And the red haired girl headed out of the cafeteria, leaving her food behind. Emily and Lillian both stood up as Charlie turned to see Liz walking out.

“I'm going to go find her,” Lillian looked at Emily who sat back down in her seat.

The pink haired girl soon disappeared behind the cafeteria double-doors. And Emily and Charlie were left alone at their table. The minute Lillian was out of sight, the blond girl kicked Charlie's other shin.

“Ow!” Charlie exclaimed, looking at Emily with confusion, “What did you do that for?”

“I don't know… You've upset Liz, somehow.”

“You don't even know what I did!”

“Exactly.”

“Then why?” he said, rubbing his kicked shin, “Maybe it's you guys who have upset her!”

“Fine, then you can kick me too.”

“Why would I do that? You're being, like, ‘Liz' weird and that's a lot of weird.”

“See!” she exclaimed, pointing a finger at Charlie, “You always roast her!”

“What is the point of this conversation exactly?”

“Look, all I'm saying is, you're the one who always throws snide remarks towards Liz…” she said and stopped talking abruptly.

The forks clattered against the many many plates in the cafeteria, there was a lot of chatter and occasional yells from the students, as well as the teachers. After a few moments of silence, Charlie stood up with his and Liz's trays:

“Well, I better go, don't want to be late for literature…”

He then disposed of the plates, put the trays on top of the big stack on the trashcan and disappeared behind the double doors.

\bigskip

The bell rang, indicating that Charlie was late for literature… again. The hallways emptied away almost instantly, not a single soul left. And then there was Charlie, rushing down the staircase, his sweater askew, his shoelaces untying.

“Wow, how am I late again?” he muttered to himself, as he skipped a few steps and turned a corner to continue running down the staircase.

What stopped him dead in his tracks was a mass of bushy red hair. It was unmistakably Liz sitting on the top step: her checkered cardigan and black skirt was to be seen beneath all the messy hair. As he climbed down the steps – not in a rush anymore – he noticed that she was sitting with her back curved, and not straight like always, scrolling through pictures on her phone.

“So I'm guessing Lillian and Emily weren't able to find you?” he asked with a half smirk on his face, stopping at the step where the girl sat.

She looked up, surprised at the sound of Charlie's voice, but turned back to her phone.

“Why aren't you in class?” Liz questioned.

“I'm late, what's your excuse?” he answered.

“My next class is with Emily,” she stated.

“And that is a problem since when?” he wondered, sitting down beside her.

“Since today.”

“Because?… Come on, do I have to force all the answers out of you?” he added with a smile.

“Because I don't want to see her right now,” she replied, ignoring the last sentence Charlie said.

“Alright… What about Lillian?”

“Don't want to see her either.”

“Do you mind me being here?”

“Not really,” she said and then, looking at him, added, “Sorry I snapped at you like that. During lunch I mean.”

Instead of saying anything – or doing anything normal – Charlie awkwardly reached his hand to wrap around Liz's shoulder, uncomfortably patted it and had a weird moment of deciding whether to remove it immediately or let it stay on the shoulder for a while, resulting in awkward and sharp movements at which Liz reacted by sighing and then placing her head on his shoulder.

“Oh, we're doing that… okay…” he said, blinking fast and opening his mouth slightly in surprise.

“So what's up with this game of hide-and-seek?” he added a moment later.

“What do you mean?”

“Well… You have run out on Emily and Lillian twice today… Is something wrong?”

“I don't know, just feeling weird and freaked out.”

“You should probably talk to them about it, Emily keeps telling me that talking about your problems makes it less scary,” Charlie looked down at his lap where one of his hands was lying (the other one being wrapped around Liz's shoulder), lifted that hand, reached it out and turned it over, palm up, looking at how calmly it stayed in the air, “I don't believe her, though.”

“Why not?” Liz lifted her head from his shoulder and looked at him.

As he retreated his other hand to his lap, he was now holding both of them out, looking at how perfectly still they stayed in the air by themselves with no support whatsoever.

“Long story,” he answered simply.

“I'm not in a rush,” she replied, turning to him.

He looked at her, biting the inside of his cheek and suddenly got up:

“Yes you are, and I am too!”

“What?”

“Our classes!”

“Oh, I don't want…”

“Oh no no no, you're going!” he said urgently and pulled her to her feet, then pushed her down the rest of the steps and left her in the hall, running towards his classroom with the words: “You'll tell me what happened during your lesson next break!”