The sun was up high when Charlie finally exited the school building. Though it was reflected in almost all of the windows of the surrounding houses and was trying to blind Charlie again, he could still see a blond girl standing painfully close to a taller boy, talking to him.

And still, Charlie walked down the stone steps and joined Emily and her boyfriend.

“Hey, dude,” Matthew greeted Charlie with a smile, reaching out his hand.

“Yeah, okay,” Charlie said, ignoring Matthew's gesture because he never really understood the handshaking thing that guys do when they greet each other.

When guys notice each other, even if they're thirty-two meters apart, they absolutely HAVE to shake hands, or else they'll die. Charlie wasn't sure what the big deal was, so he never shook hands with anyone, and he wasn't going to make an exception for Emily's boyfriend.

Charlie knew that the moment he would turn his head towards the blond girl, he'd see her reproachful glance, so he changed the subject quickly, avoiding her eyes:

“So, where is Liz?”

“She'll be here in a moment,” Emily answered.

“So you talked then?”

“Well, she told me that you skipped class,” she said, sounding very disapproving, but then her voice softened, “But it was actually really sweet that you did it for her.”

Charlie smiled but that smile faded very quickly once Matthew put his arm around Emily's shoulders and hugged her.

“Did she tell you everything?”

“What?” the blond girl said distractedly but then, refocusing, continued, “Oh, well, she just told me that she felt better after you talked to her—I don't know \textit{what} you could have possibly said—but she still won't tell me what's wrong…”

“'Cause that's between Charlie and me. Right, Charlie?” The familiar bushy mass of red hair appeared behind Emily's back as the blond girl turned around in surprise.

“Um, sure, I guess… What…” Charlie started but was cut off by a car honking somewhere in the distance.

Matthew, as if awakened by the noise, jumped on the spot.

“Oi, I forgot! It's my mom. She's been waiting for a long time, probably… We better go,” he said, turning to Emily.

“Alright, well, we'll see you later,” Emily waved good-bye to the two friends who were left behind.

“What? Go where?” Charlie began, but it was too late: Matthew and Emily were already sprinting towards a bright-yellow car.

“Well, it's just the two of us now,” Liz said, turning to him with a smile once the couple was out of earshot.

“Oh boy,” Charlie sighed, turning around and heading in the direction of his house.

“Good idea. You can tell me all about your 'story' on the way!”

“I wasn't going to.”

“Alright, I can go first,” Liz said, ignoring him.

“Please don't.”

“I thought you were interested!”

“I am, but I don't want to tell you my 'story' afterwards,” Charlie sighed.

“Why not?”

“I'm sorry, it's not something I like talking about.”

“Well, maybe I don't like talking about whatever is going on with me!”

“But you want to tell me?” Charlie turned to her in surprise, as they passed a building, the walls of which were covered in graffiti.

“Yeah.”

“Why?”

“There's no reason… I guess I'm just comfortable telling you.”

Charlie wasn't sure how to react. He looked down at the pebbles that were crunching under his bright-pink sneakers.

“Okay, um… sure, we can tell each other our 'stories',” he said to her after a minute.

“Alright, I'll go first.”

Charlie nodded. Liz looked a bit nervous, so he patted her on the shoulder approvingly and then put both his hands in his pants pockets. And while he expected her story to be long and tear-stained, it was very short. Too short.

“I cringe a lot in our… um… relationship with Lillian,” she said, clearing her throat repeatedly.

She looked very confident, as if she had just explained everything, including the smallest of details. But the truth was Charlie hadn't understood a thing and was thoroughly confused.

“I'm sorry, I don't completely understand.”

“Okay, well, Lillian is very thoughtful and gives me a lot of attention.”

Charlie turned around to face her, furrowing his eyebrows as he did so.

“And that is bad \textit{how} exactly?”

“Well, like, she keeps telling me that I'm beautiful and that she really likes me,” Liz said, starting to sound frustrated.

“I still don't see the big deal,” Charlie sighed and quickly added, “Sorry.”

“It's like when she says 'I like you', I am obligated to say it back and…”

“You don't feel the same way?”

“No, that's the thing, I do! I do really like her, but it makes me very uncomfortable.”

“When she says 'I like you'?”

“Not just that! She keeps giving me flowers or passing me notes in the middle of class, saying 'Thinking of you' or something cheesy… Ew,” Liz said with a disgusted face.

“Alright… I… erm…”

“You know what, you don't have to answer or say anything. Even \textit{I} don't know what's going with me.”

“Really? 'Even'?”

She merely smiled and shrugged in reply.

“Well, she's just expressing her feelings this way, but if you're not comfortable with that, you should tell her,” he replied.

“I don't want to… or at least not until I figure out what's going on…”

They walked in silence for a while with the street being very crowded. You could see people sitting outside of cafes, drinking tea or coffee and sharing some sort of interesting gossip.

“Well, then, it's your turn,” Elizabeth interrupted the peacefulness of it all.

“Oh, right…”

There was a pause.

“Um… well, to make a long story short… I've been having panic attacks,” his voice croaked the words out.

“Oh.”

“Yeah…” Charlie looked down at his feet.

“Do you mind me asking…?”

“Sure, go ahead, why not,” he shrugged.

“What are they like?” she questioned carefully.

“They're like…” he started, looking into the distance, trying to find the accurate words, “You just sit there, doing your homework and then you feel like you will never breathe again like you did before and you believe that you're going to be stuck like that for the rest of your life, not knowing what to do, how to get out, \textit{wanting} to be free and get out but continuing on being lost in your own mind…”

“That must be horrifying…” she whispered gently, looking at the boy sympathetically.

“It is… But they aren't like… I mean… It's not like they're painful, well at least not for me. They're just weird and not the most pleasant experience of your life.” He blinked and then cleared his throat afterwards.

“I'm really sorry.”

They passed a few more buildings and could see Charlie's house in the distance. The people around them squirmed about, all in a hurry somewhere. Everyone always seems to be in a hurry as if time is running out. And it is.

It's probably obvious that almost every person on Earth knows this—time \textit{is} running out. Charlie discovered it by himself and then had told Emily—she, apparently, hadn't noticed it on her own. He hadn't told anyone else, though. But he had a feeling that the girl walking next to him understood the concept without the need for it to be declared out loud.

“There's one thing I still don't completely get,” she said suddenly.

“What's that?” Charlie sighed.

“Why were you looking at your hands when we were sitting on the stairs?”

“Oh, erm… well, I guess it's sort of a habit of mine,” he explained, “Every time I get bad anxiety, I hold out my hands in the air to check if they're shaking.”

But after Liz gave him a confused look, he rolled his eyes and added:

“It's one of the symptoms of a panic attack.”

She opened her mouth and closed it just as quickly. She then stopped walking, making Charlie stop too.

Liz opened her arms and embraced him.

He couldn't remember the last time a friend had hugged him.

“I'm sorry you're going through that,” she said.