The next day began unlike any other day in Elizabeth's life. After she woke up, rubbed her eyes and stretched, she felt some kind of relief, as if something had been lifted off her chest. She also felt much closer to Charlie. Yes, he had insulted her before, but she knew all along that it was just his way, and now she felt even better about him.

Once she got to school that day, she found Charlie in the hallway and gave him a hug.

“What are you doing?” he asked her.

She just smiled at him and walked away.

Recovering from this unexpected gesture, the ash-brown haired boy didn't have a chance to notice Emily coming up to him.

“What was that all about?” she questioned.

“Don't know,” he replied, slamming his locker door.

“Oh, shoot!” she exclaimed out of the blue, as if remembering something she had forgotten about, “I've got to get going… We'll talk later.”

\bigskip

When Charlie was walking to his next class, biology, he noticed a blond girl and a redhead approaching him. They were chatting about something, as always, and hadn't noticed him until they were three meters apart. That was the exact moment when Liz looked up at Charlie and automatically spread her arms open to come in for a hug.

“What the hell are you doing?” he asked calmly, stepping aside before the girl could embrace him.

“I was just about to hug you,” Liz stated, a little befuddled.

“Now, now, that's enough out of you.”

“What's 'enough'?” Emily piped in.

Charlie kept silent, wishing they'd let him go to his class.

“Hello? Earth to Charlie!” she exclaimed.

“Liz hugged me at school,” he mumbled, loud enough for Emily to hear.

She reacted instantly, raising her eyebrows.

“What did you hug him for? Do you want to die or something?” she asked, talking to Liz.

Charlie looked at her with the same reproachful look that Emily herself liked using against him. He didn't \textit{mind} being hugged, but not in front of everyone. That is, not in a public place.

“What do you mean?” Liz questioned.

“He doesn't like public displays of emotion.”

Without thinking, the ash-brown haired boy pushed past Emily and Liz. How he wished they would shut up about emotions and hugging! It was unbearable to listen to people talk and ask about his feelings. They aren't meant to be the topic of discussion.

\bigskip

It was tradition for Emily to search for her friends once classes had ended on Friday and gather on the school grounds to laugh and just have a good time. She was standing under a tree, hiding from the direct sunlight, almost like a vampire, with Matthew's arm wrapped around her shoulders. Lillian and Liz were there, as well as some other friends of Emily's, all cracking up about something.

Charlie's traditions varied. Every time he stepped out onto the school's stone steps, he looked up at the sky, whether it was winter and very dull or late spring with the sun burning his eyes. He didn't have as many friends and, seeing as he was frustrated with the only two he \textit{did} have, he walked right past them towards the path leading to his neighborhood.

“Hey, Charlie! Over here!” called a familiar voice from the direction of that tree.

Turning around, he wasn't surprised to find Emily waving at him. He walked back towards the massive trunk and stopped between Liz and Lillian.

“Hey, dude,” Matthew said.

“Yeah,” Charlie answered, raising his eyebrows and tilting his head as a sort of greeting.

“Matthew, you were saying?” a boy suddenly exclaimed.

“Oh, right! So get this: Em and I were getting some fro-yo and then this crazy guy barges in, makes up some lame excuse and drags her out on the street!” Matthew chuckled.

Everyone laughed, except for Emily and Charlie. She threw Matthew a sideways glance, which he didn't seem to notice, and stepped aside so that his arm didn't touch her shoulders, which, it seemed like, he didn't notice either. Charlie merely stood there, narrowing his eyes at his best friend's boyfriend.

“Remember, \textit{Charlie}?” Matthew added out of the blue.

“\textit{Vividly},” he answered, a fake smile plastered onto his face.

“That… that's not very nice,” Emily stuttered.

The words, though quiet, echoed in the air. Everyone stopped laughing suddenly. She looked seriously at Matthew.

“Oh,” he sighed in return, “I'm really sorry. Really.”

“It's okay. Everyone screws up sometimes…” she said glumly, “Anyways, I think we have to go. We still have homework to do before we... you know. Right, Charlie?”

“Yeah,” he said, lightening up as Emily approached him.

His mood changed just as quickly when Matthew walked over to the blond girl.

“No, I really am sorry. I hope you're not mad,” he stated.

“I'm not the one you're supposed to be apologizing to,” she said, looking at her friends, who carried on talking to one another.

“You're right. I'm sorry, Charlie. I never should've said a word.” Matthew walked over to him.

The ash-brown haired boy looked at him blankly, pretty sure that the apology meant nothing. Matthew then turned to Emily and continued.

“Let me walk you home,” he suggested.

“Erm… sure…” she agreed reluctantly.

And once again, poor Charlie was left all alone, while the other two walked off in the direction of Emily's house.