“Wow, it’s… um… Beautiful?” Matthew said out loud.

They did all think the same thing, even Charlie. The house they were standing in front of was crooked and shaggy and that is said in the nicest way possible, because honestly it was almost a complete wreck. ‘Almost’ because it hasn’t collapsed just yet. But, as the three venturers stood before it, eyeing it anxiously, they were sure that the ancient building would fall apart the moment they’d so much as sneeze.

“So we’re just gonna go inside?” Matthew spoke again.

“That’s the plan,” Charlie rolled his eyes.

“Hey, are you guys sure we packed enough things?” Emily asked.

The two boys looked at her weirdly. The girl with a backpack the size of a mini fridge on her back looked at them back questionably.

“You’re literally ready to climb Mount Everest, so I’m guessing yes. Yes, you did pack enough,” Charlie answered incredulously.

“Don’t go judging. You guys are the ones who didn’t even care to bring so much as a flashlight!” she snapped.

“I didn’t need to bring one, you’ve packed five flashlights AND thirty six batteries,” Charlie said.

“That is called precaution,” she told him.

“That is called paranoia! You brought matches, a log, a tea kettle and even a mini basket of muffins with the basket. And that’s not even half of it!”

“What was I supposed to do? Not bring all this? Not come prepared…?” Emily started.

“Well, yeah!” Charlie cut her off.

“Oh, okay! So if you’ll hurt yourself while recklessly ‘exploring’ your sturdy little house over there, you won’t need my first aid kit?” she asked rhetorically.

“No, I won’t because it’s stupid! You took every item you could find that was lying around your house!”

“Why are you shouting?”

“I’m not shouting, I’m simply telling you that you don’t need to bring everything and everyone you can find in order to go into a house!”

“Oh my god, is this because of Matthew?” she asked.

“No! No! Why ever would you think that?” he said skeptically.

“You said you didn’t mind!” Emily shouted back at him.

“Guess what? I lied!”

“Well, I’m not surprised!”

“What do you mean you’re not surprised?! I’ve never lied before that!” he said furiously.

“Oh yeah?”

“Yeah!”

“How about the time you stormed in on me and Matthew in the frozen yoghurt shop and LIED about the imaginary news program you saw on TV?” Emily shouted, “Right, Matthew?”

She turned around to the spot where the boy was standing moments ago only to find him crouching on the ground, his hands over his head.

“Matthew?” Emily called again, now squatting down beside him.

No answer. He was pulling at his curly hair, his hands covering his ears. His head was stuck between his knees.

“Matthew, what’s wrong?” Emily questioned, looking over at him with concern, while Charlie muttered something like ‘unbelievable’ under his breath.

“Can we just go inside already?” Matthew finally said, straightening up.

“Um, sure… Are you okay?” Emily asked.

“Yeah, I just… uh… um, well I got a little dizzy, that’s all,” Matthew answered, blinking furiously.

He rubbed his eyes, shook his head and took a deep breath. And then moved closer to the broken porch. He motioned his hand for the other two to come.

Stepping closer to the door, they could now see some words carved into the its stale wood.

“‘Residence of Mr. M’?” Charlie read out loud, “Who’s Mr. M?”

“Do you really expect me to know?” Emily looked at him, irritated.

“I was just asking, no need to be worked up over nothing,” he replied.

“Let’s just get this over with,” she groaned and opened the door.

The screech the door let out echoed in the spacious room that stood before them. With the light coming from the broken windows all around they could easily make out the grand staircase that was precisely in the center of it with a doorframe to its left and an open room to its other side. There was a chandelier hanging from the ceiling to the right, sparkling in the sunlight that was pouring through the windows and open door. The staircase was carpeted and decorated with some sort of peculiar ornaments on the banister.

Matthew carefully closed the door behind him and looked mysteriously up at the second floor. His eyes were narrowed and still fixed on something upstairs when he said:

“Hey, why don’t we go into that room first? Looks like a kitchen.” And he gestured to the room on the left.

Emily nodded and was already heading towards the supposed kitchen. Charlie went to go after her but could see, from the corner of his eye, Matthew sneaking away towards the ancient staircase. Charlie looked at Emily, already examining the contents of the kitchen drawers, and then back at Matthew, thought for a minute and went after the curly haired boy.

Charlie reached him in no time and grabbed him by his wrist. Matthew jumped in surprise at the sudden touch and, turning around, looked Charlie dead in the eye.

“Where do you think you’re going?” Charlie asked in a low voice, holding a firm grip on the boy’s wrist.

“I thought we were here to explore, so I’m exploring,” he answered with an unpleasant look on his face, all the while climbing the staircase.

“You literally just told us to go ‘explore’ the kitchen,” Charlie hissed, moving up the stairs along with him, “You are up to something.”

“How could you even think such a thing!” Matthew exclaimed in a fake tone.

“So you are!”

“No, I’m not, I just told you so.”

Charlie squeezed his wrist even more so.

They were now almost at the top of the staircase, glaring at each other.

“Anyways, you better go… what if something happens to Emily!” Matthew smiled.

“WHAT? What did you do?” Charlie wanted to hit the smirking boy so bad.

“Nothing. I’m just here to explore, why would I do something to my girlfriend?” he asked rhetorically.

“You do know that Emily will be informed about this conversation?” Charlie said through gritted teeth.

“Oh, I very much doubt she’ll believe her lovely boyfriend could’ve possibly done something wrong!”

“If so much as a hair falls off of her head, I will literally kill you.”

“Alright, that’s fair,” Matthew chuckled and then, coming closer to Charlie, added: “But if I were you, I wouldn’t leave Emily for the sake of her safety.”

The ash brown haired boy could feel his heart beating against his rib cage, something stuck in his throat. But he couldn’t show any sign of weakness.

“Then you go and protect her from all the dangers, I mean, you are the boyfriend, aren’t you?”

Matthew stood there, as still as a statue, not moving a muscle, not showing a single emotion. Charlie glared at him, then, without turning his head, slowly walked downstairs, watching Matthew all the while.