Emily was standing near the kitchen doorframe, her arms crossed on her chest.

“Where have you been?” she asked him as Charlie turned the corner and found himself come face to face with the frustrated girl.

“Listen, we have to get out of here right now!” he told her, rushing through the words with worry.

“Are you messing with me? You were begging me to come here and now you suddenly want to go home! What, did you see a ghost or something?” she said, sounding very much annoyed.

“No, you don’t understand,” he continued, looking around at the staircase, “Matthew is up to something!”

“Wow! I would have never known! Tell me, does this have anything to do with you not liking the idea that I invited him here?” she questioned incredulously, “Where is he, by the way?”

“No time for that, we need to leave!”

“So you want to leave Matthew here?”

“Or make him leave the house.”

She shook her head in disbelief at this nonsense. What was up with Charlie was a great mystery for her. She sighed and wrapped her arm around his shoulder.

“Come on, let’s go find him,” she said in a comforting tone.

“Find whom?” came Matthew’s voice from behind them.

Charlie jumped, frightened, while Emily walked over to hug the auburn-haired boy.

“You’re okay! Where were you?” she asked her boyfriend, still clinging to him while her best friend was trying to get her away from ‘danger’ by pulling at her arm.

“Uhh, you know, just… well… trying to find the bathroom,” he replied in what was supposed to be an uncomfortable tone.

And he smirked at Charlie who, in return, looked him dead in the eye with his jaw clenched.

It was weird being threatened by somebody when you didn’t even know what they did, plus they didn’t threaten you exactly, but Charlie could feel all the tension uprising in the still air. Emily didn’t seem to notice all the glaring because the next thing she said was a bit strange, considering the circumstances.

“How about we go upstairs?” she proposed.

“Um…” Matthew started, pushing away from Emily’s tight embrace, “How about we rest for a while?”

“But we just got here…” she said, furrowing her eyebrows.

“Well, uh… remember the outside? When I fell down right before we went in?” he started.

“Was that you FALLING DOWN?” Charlie wondered out loud, crossing his arms on his chest.

“Yes,” Matthew answered, “indeed it was. So, anyways… I think I’m dehydrated or something…”

“Why were you searching for a bathroom then?” Emily questioned, confused.

“Yeah, Matthew, why were you searching for a… bathroom, you say?” Charlie leaned forward, his arms still crossed on his chest.

“You can be dehydrated and still need to go…” Matthew replied, narrowing his eyes.

“Alrighty then,” Emily said, “We can stay here with you while you rest.”

Charlie was about to explode from the unfairness of it all. Why wasn’t Emily at all concerned with this sort of behavior?

But as Matthew sat down onto the moldy floorboards with Emily seating herself beside him, Charlie opened his mouth in the surprise that came with the plan that was just formed in his head.

“Great!” he exclaimed loudly.

“What? What is it?” Emily questioned.

“Now I have to use the bathroom!” he answered.

Matthew opened his mouth in anger. Charlie made a face at him while Emily looked at the two boys with concern.

“Hey, you know what?” Matthew started as Charlie climbed up one step of the staircase, “The bathroom is down the hall, on the left… Wait! You know what? I can SHOW you where the bathroom is!” And he got up from his sitting position.

“There’s no need, thank you very much,” Charlie replied with a fake smile plastered on his face.

“You can easily get lost, let me help you find it,” Matthew informed him in a sort of aggressive way.

“Then how did you manage to find the…” Charlie started quietly but was cut off by Emily.

“Well I’m not staying down here all by myself! I’ll come up with you!” she exclaimed, not hearing what Charlie was saying.

Charlie automatically looked at the auburn-haired boy. Anybody could easily see that Matthew was sort of taken aback by this and didn’t know what action to take. There was a moment of dead silence in the room with Matthew staring at a specific spot on the wall. But there was a sudden loud noise that broke the silence and echoed all around them. The noise, of course, made everyone jump as nobody expected to hear a Michael Jackson song right at that minute. It was coming from Emily’s backpack and she instantly made to rummage in it.

“Oh, it’s my phone…” she said, fishing out the object, “Liz is calling!”

She stood up and left the two boys in the hall near the staircase. Both of them stood as still as they could while Emily was walking towards the kitchen. But the moment she answered the call and the music died away, they were like two ferocious dogs unleashed.

Before Charlie knew it, he was pulled by his forearm down from the step and almost fell over. Matthew was now holding his two wrists so that Charlie was practically helpless.

“What the hell was that?” the auburn-haired boy questioned, pulling Charlie closer to him.

He then bent Charlie down and kicked him in the stomach, not letting go of his wrists.

With his face being so close to Matthew’s hands, Charlie dug his teeth into the soft light brown skin, making Matthew immediately release the hold and gasp for air in agony. That was the exact moment when Charlie, though in pain from the kick, jumped onto Matthew’s back and started flinging his fists at him.

Matthew reacted instantly, spinning around on the spot to shake the guy off and simultaneously trying to reach one of his arms for Charlie’s knee. His arm did manage to push Charlie off.

Luckily for Charlie, his reflexes were top tier and he didn’t fall down to the ground but simply stumbled.

Without delay, as soon as both of Charlie’s legs touched the dusty floorboards, he flung himself at Matthew. But this time, instead of jumping on top of him, Charlie started punching every place he could reach: Matthew’s handsome face, his shoulders, his chest… The now wincing opponent grabbed Charlie’s shirt collar and made him bend in half once more. And once again brought up the knee with all the strength in the world, but this time aiming a bit lower than the stomach.

Charlie grunted and dropped to the floor, holding his hands in between his legs. The last thing Charlie could think of doing was roll over violently from his one side to the other to reach Matthew’s feet with his legs.

And to his surprise, Matthew actually toppled over and fell down onto the stale floor, face first.

Luckily for the ash brown haired boy, as Matthew was trying to get up, Charlie heard the floorboards creak somewhere near the kitchen entrance and the next thing he saw were a pair of lavender sneakers.

“Guys…?” a voice Charlie was thankful for called, “What’s going on?”