Emily walked out of the kitchen looking as frightened as ever. When she picked up the call and left the two boys, they were smiling at her. She was in a good mood even though Liz had called to scold her about not being at home when she needed her to.

Emily \textit{did} know that Liz was jokingly mad at her so she was still in a good mood when she got back to the foot of the staircase. But she was now concerned with what she saw standing – lying, actually – before her. The two boys who looked like they were bonding before were now lying on the floor.

Charlie looked like he was in a lot of pain and his hands were sitting in between his legs. Matthew was struggling to get up.

“Hello? Did you hear me?” Emily called again, “What is going on here?”

Charlie was trying his best not to wince at the pain that Emily’s ‘lovely boyfriend’ had caused him and was trying to make up an explanation. But Matthew was faster than him.

“We had a little mishap,” he said.

Now that Matthew had turned his face in his direction, Charlie could now see what he got out of the fight: he himself, Charlie Rodriguez, had actually injured a real live person for the first time in his life! Though it was just blood pouring out of Matthew’s nose, Charlie couldn’t help but be proud of himself. Not that he liked violence that much, but seeing Emily’s so-called ‘boyfriend’ in pain brought him so much joy.

“What kind of mishap is this?!” Emily exclaimed and then, softening her voice, added: “Charlie, are you okay?”

“I’m… fine,” he croaked.

“So, um, basically… we, um… were trying to slide down the banister,” Matthew said, finally turning over and sitting up.

Emily’s eyes popped out at the sight of Matthew’s nose, soaked in blood.

“And… what happened next?” she questioned.

“Well, I fell face first and \textit{Charlie} over there,” Matthew looked over at the boy who still hasn’t recovered from the pain, “He… well, um, he… got injured… down there…”
After her mouth opened widely, Emily immediately ran to her huge backpack and fished out a couple of objects.

She walked over to Matthew and handed him a first-aid kit which she brought with her. And then crouched down by Charlie, holding an ice bag in her hand.

“You still think my precautions are stupid?” she asked.

“No,” Charlie croaked back.

She handed him the ice bag and sat down near him, on the first step of the staircase.

“So what do we do now?” she questioned loudly while Matthew stuffed his nose with  cotton wads.

“I still need to use the bathroom,” Charlie informed, now sitting up with the ice bag seated in between his legs.

“Still?” Matthew looked at him disapprovingly, “Wouldn’t the injury make you not want to go?”

“No,” he answered, raising his eyebrows at Matthew, “I still need to use the upstairs bathroom.”

Emily looked at them with more concern than ever. Was it possible that they earned a concussion during this ‘mishap’?

“You know,” Matthew started again, “there’s no need to go upstairs when there’s a bathroom downstairs.”

“How do you know there’s a bathroom down here?” Charlie asked suspiciously.

“Oh, I don’t know,” he replied sarcastically, “Maybe because most houses have two bathrooms?”

“No, they don’t,” Charlie stated.

“Alright…” Matthew sighed, “How many bathrooms do you guys have?”

“Uhh… two,” Emily said.

“One,” Charlie informed.

“Well I have two,” Matthew smirked, “You see, Charlie, I win.”

Somehow, Charlie knew that Matthew wasn’t just talking about the bathrooms.

But he also knew that he wouldn’t survive another fight like that.

“Alright,” Charlie said grumpily, “Lets try to find a bathroom downstairs and if we don’t, we’ll go straight upstairs.”

\bigskip

The open room to the right of the staircase, the one with the big chandelier, was carpeted. The carpet bore a set of strange ornaments, matching the ones on the banister. It was obviously a living room: in the middle, there stood a big teared up couch, a coffee table, and two armchairs. Along the walls were countless book shelves with twice as many books.

Dust and mold were the main components of the room, though.

Emily walked over to one of the shelves and studied the titles carefully. Matthew stopped to look at the crumpled up pieces of newspaper that were lying on the coffee table.

“Wow, these books are really old, ancient even,” Emily informed, turning around to face Charlie.

“Um, hello?” the boy called, “Aren’t we supposed to search for a bathroom?”

“Oh, right, sorry,” and she followed him out into the hallway.

The hallway was on the opposite side of the entry to the living room and was very narrow and dim-lit. There was only one door at the end of the hall. The three explorers stopped in front of it and looked at each other cautiously.

“Why don’t \textit{you} open it, Matthew?” Charlie suggested, feeling safe in the presence of the blond girl who, in turn, was looking at the door apprehensively.

Matthew, though reluctant, reached his hand out to the doorknob and pulled. With a terrible creak the door revealed a room so small, that the three of them wouldn’t be able to fit in it even if they really wanted to.

And even though there wasn’t much light, they could still make out the metal bar that was stuck in between two walls. It was a closet.

“These are also quite old,” Emily said, flipping through the vintage clothes that were hanging on the rusty racks.

“This is not a bathroom…” Charlie informed in a sing-songy way.

“No kidding,” Matthew retorted sarcastically.

“No, but look!” she indicated at a summer dress with embroidered flowers, “This is the only dress with a different size, the others are all two sizes bigger and not dresses.”

“And?” Matthew raised an eyebrow.

“That means this is a woman’s dress, the only woman’s dress here.”

“I still don’t get it.”

“Look down here!” Emily said, frustrated, “There are no shoes that are the same size that would supposedly fit the dress’s!”

“I’m confused,” Charlie stated.

“Isn’t it obvious? The wife of the photographer who lived here left in a hurry! Isn’t that peculiar? It’s like she didn’t exactly disappear but simply left the house!”

“Oh, come on, don’t play detective,” Matthew said carelessly, “If you want the dress – just take it, or whatever it is you girls seem to want?”

“Excuse me?” Emily and Charlie asked in unison.

“What?” Matthew continued on with his rudeness.

“She is not playing detective, she might actually be onto something,” Charlie narrowed his eyes at the boy standing near him, “What the hell is your problem?”

“What’s my problem?” he raised his eyebrows, “What’s your problem?”

“My problem is that you are being a total jerk,” Charlie was now glaring at the auburn-haired boy.

“Okay, you know what, guys? It’s fine, let’s go,” Emily piped in, trying to be as nice as possible, though Charlie could sense she wasn’t exactly content with Matthew’s phrase. On the other hand, she gave Charlie a soft smile.

After the closet door was closed, they all turned around and walked back up the hall. The sunshine was pouring through the living room windows and you could see rare slits of it in the small hallway.

Amongst the floral wallpaper on the wooden walls of the corridor there seemed to be something glistening, rather softly, in the afternoon sun. As the other two didn’t seem to notice a thing, Charlie stopped and deliberately pointed at the spot.

“Hey, look, there’s something here,” he informed as he dusted the glistening object on the wall.

“Oh, hey!” Matthew exclaimed loudly.

While the other two gave him a look, he didn’t seem to notice it and continued to stare at the object.

It was a photo of a smiling baby.

With the background of the photo being green and the wallpaper being of the same color it would be hard to notice there was a picture hanging there even if the glass of the frame wasn’t covered with a thick coat of dust.

“It’s probably just the kid they had,” Emily stated firmly, “Nothing special.”

“Exactly! It’s absolutely nothing special,” Matthew agreed loudly and quickly walked away into the living room.

Charlie looked at the back of Matthew’s head and then at Emily who, in return, raised her eyebrows in surprise and took a deep breath.