“Well, there's no bathroom down here…” Charlie started with visual excitement, “Which means we have to go upstairs!!!”

Matthew pretended he couldn't hear the boy's words and kept looking at the books' spines on the shelves.

Emily and Charlie were already at the foot of the staircase and Matthew still hadn't come out of the living room.

“Matthew!” Emily called, “Are you alright?”

“Yes, yes, I'm fine,” he said, still not showing up.

“Then what are you doing in there?” Charlie asked loudly in a cross tone.

“I'm exploring!” he answered back in the same aggressive way.

“Matthew, we are trying to find the bathroom, if you're not coming with us, we're going without you,” Emily stated firmly, making Charlie look at her admiringly.

The blond girl's statement, of course, made the right impact, as she intended it to. Matthew appeared in the hallway as soon as she finished her sentence. Though Charlie could see all the anxiousness reflected in Matthew's movements, Emily didn't seem to notice a thing.

And so, without uttering a word, they had finally started to climb the stairs to explore the second floor. The climb wasn't even that long, but Matthew was out of breath instantly and by the time they got to the upstairs landing, he was ready to collapse.

The landing they were all standing on was also carpeted, and the ornament was the exact same as the one on the banister and the living room floor. There was a door on the left, two doors right in front of them and another door on the right.

“So… which one is the bathroom?” Charlie wondered.

“We can open each door to see…” Emily started.

“No need!” Matthew quickly cut her off, “I've been to the bathroom, remember?”

And he walked over to the door exactly to their left. At first, it refused to be opened, but after Matthew's frustrations and pathetic-looking attempts, it finally revealed – with a terrible creak – what was once a clean, white bathroom.

What came next was a surprise for Charlie: Matthew took his arm, led him to the doorframe and pushed him inside the bathroom. Emily frowned at this and was thoroughly confused with her boyfriend's behavior, but decided to keep quite for no apparent reason.

Charlie, being disoriented as he was, wanted to protest and get out of the bathroom, but the door was slammed right in his face before he knew it.

“We're gonna wait for you here!” Matthew called maliciously from the other side.

Did Charlie really need to go to the bathroom? Of course not. But he had to pretend, or this 'play' was worth nothing.

Now, whether or not did Charlie want to touch anything in this particular bathroom was a different problem altogether. Standing opposite the door was a dirty sink, covered in green and black mold. Near it was a dusty drawers unit, and across this unit stood the toilet.

It was utterly disgusting, it actually made Charlie want to puke.

And in the farthest corner, opposite the toilet, stood the revolting-looking bathtub with a fuzzy rug, which had probably seen better days.

The toilet paper had holes in it, so he wasn't even thinking of touching that.

So after waiting for a few seconds, he walked over to the toilet and pressed the button with his elbow. The toilet rattled, but had not flushed anything. Instead, Charlie saw a few insects crawling out from behind the rattling object.

“Gross, gross, gross,” he whispered to himself and went to turn the water of the sink on.

The water that came splashing out of the faucet was dark-orange, brown even, and hissed at him terribly.

That was worse than seeing ghosts and Charlie hurried to close the faucet and run out of the wretched place.

“Hello there,” Matthew exclaimed.

“Yeah,” Charlie didn't looked too pleased with the smiling boy.

“So you've finished, I'm assuming?”

“Yes.”

“Great! Now we can all go home,” he said with a big dumb smile on his face.

Emily and Charlie exchanged a confused look. They had just gotten to the house an hour ago and they both wanted to explore the whole construction through and out. Matthew was the one tagging along. So he was excited to get here only to use the bathroom?

“What do you mean 'go home'?” Emily questioned.

“I mean, I want to go home and I'm pretty sure you do too,” he answered as-a-matter-of-factly.

“No, we do not,” Charlie stated firmly, looking at Emily, who nodded in agreement.

“Yeah, Matthew, what's wrong?” the girl asked worriedly.

“I'm just kinda tired,” he said, yawning.

“Well, I mean, we can sit here and rest for a while, we're not in a hurry…” Emily told him uncertainly.

“Why can't we go home?” he asked.

“Firstly, because I promised Charlie I'd explore this house with him. And I keep my promises,” she started.

“One way or another,” Charlie finished for her.

“Anyways,” she continued loudly, looking over at Charlie reproachfully, “And secondly, I kind of want to become a sort of detective for a while, I mean, isn't this whole 'disappearing mystery' thrilling?”

“Yep, it sure is,” Matthew said, emphasizing every word.

Emily looked over at Charlie in confusion for the umpteenth time. The boy merely shrugged his shoulders in reply. He could actually tell her that something was going on, but seeing as she hasn't brought up their downstairs conversation at all, he figured she still doesn't believe that the guy who's acting weird all of a sudden is up to no good.

“Welp, it's no good wasting our time up here without going into any rooms, so let's,” Matthew said suddenly and motioned to the door closer to their left in front of them.

Charlie was the one to open the door this time. The handle was so stale that it didn't want to turn itself at first. But that was no obstacle for Charlie who was determined to find out Matthew's 'secret', if there was one.

The door opened to a relatively big room. Right in front of them stood a faded out beige vanity mirror with a matching leather chair. It appeared to be the bedroom of the photographer and his wife as there was a king-sized bed standing under the only window. There was a bedside table, a broken lamp and a closet with so many drawers, one could count them for eternity.

Charlie instantly started scanning the room for suspicious – or at least interesting – objects. Fortunately for Matthew, he wasn't able to find any, until…

“Hey, look!” Emily exclaimed, “There's a photo of all three of the family together!”

The two boys were at Emily's side before they knew it. She was kneeling down beside the bedside table, the only drawer wide open, and was holding a framed photo in her hand. A young woman and a seemingly older man were hugging a baby. They were all sitting on a blanket in a park, laughing.

“His face looks kind of familiar,” Emily pointed at the man.

“Yeah, I think I've seen him before, too,” Charlie stated, “Must be some famous photographer or something.”

“Yeah, probably,” the girl agreed, and put the picture back in its drawer.

“Well, we've looked at pretty much everything in this room, so we can go home now?” Matthew wondered loudly.

“Firstly, we haven't looked at everything in this room, and even if we did, we still have those two rooms to 'look at',” Charlie said crossly.

Emily, obviously choosing to ignore Matthew's strangeness, went over to the closet and started opening all of the drawers.

“Woah, what are you doing?” he exclaimed suddenly.

She turned to face him, looking over at Charlie with confusion. But Matthew went all quite and didn't even try to explain his outburst.

So Emily continued looking into every drawer she opened. Charlie bent over beside her to examine the contents closer. The other boy continued to stand next to the bedside table. Once all the drawers were opened, Emily sighed and gazed at Charlie to see what he thought.

“Well, this just proves my earlier statement which is even more peculiar,” she said finally.

“What are you talking about?” Matthew questioned from behind.

“That the wife left in a hurry!” she exclaimed and beckoned Matthew to the closet.

He came over, looking thoroughly confused. Charlie too, wasn't comprehending, and Emily could see.

“Look, in these bottom drawers: they kept their socks here. And the old guy's drawer is full, but the woman's has just two mismatching socks!”

“And?” Matthew asked.

“Well unless she used to wear mismatching socks which I highly doubt because she looks like she cared about her looks a little too much, then it's perfectly fine!” she sighed, exasperated.

“And then in these drawers over here – they kept their jewelry. This one (she pointed to the drawer in question) was obviously hers because there is a single earring here and some kind of pearl from a necklace, I'm guessing…” she continued.

“Alright, alright, fine, thank you, I got it. You don't have to play detective anymore,” Matthew exclaimed quickly, “Are we done now?”

“Um, yeah, I think we've looked at everything in the room,” Emily answered, standing up.

They were headed to the door. But Charlie, taking a look around the room, noticed something else.

“Wait!” he said, “We haven't looked in the vanity mirror drawers.”

“Oh, right!” Emily rushed to it while Matthew gave Charlie a dirty look.

The drawers were not allowing Emily to open themselves. She jiggled the knobs in frustration but it looked like they were glued into the whole construction.

“Maybe it's a sign to not open them?” Matthew suggested, patting the girl's shoulder.

But Emily was determined to find out what was in them. And when Charlie proposed he'd help, she shook her head. She did want to open them herself but after about a few minutes of trying and failing miserably, she let go of the knobs and kicked the wooden leg of the vanity mirror.

“Boy, somebody has issues,” Matthew murmured and unfortunately for him, Emily heard every single word.

She wanted to say something and was opening her mouth when she noticed that the drawers were now ajar. The kick must've done it and she was set to finish the process. She kicked the same leg once more and, waiting for the drawers to come looser, was disappointed that nothing changed. Emily kneeled down and started jiggling the leg with her hands. Nothing happened.

“Somebody, please, help,” she called.

Charlie grabbed the other leg and they both started jiggling it together. The drawers opened ever so slightly.

“We need more…” Emily started saying but was cut off by her own thoughts.

She then suddenly stood up, took hold of the leather chair and started beating the table of the vanity mirror. The surface-hitting did nothing except scare the living hell out of the two boys.

So the blond girl began to hit the front legs of the vanity mirror.

Before she knew it, there was a loud 'CRASH' and the two legs had come off the whole construction, making it topple over in front of Emily. She instantly dropped the leather chair and jumped back only to realize in a few seconds that the drawers opened up completely.

The three of them, all in shock, rushed closer to the fallen over vanity mirror to get a better look at the contents of the drawers.

“Empty…” Emily said, out of breath, “They're both empty…”

“So all this was for nothing,” Matthew waved his hands, motioning at the broken legs.

“I know that, thank you,” she answered very slowly, giving him a dirty look.

The blond girl took a deep breath and rubbed the bridge of her nose. While the other two stood up, she continued to sit on the floor until Charlie offered his hand for her to get up.

She took it and, still being in shock of herself, stood up, dusting off her pants.

“Well,” she started uncomfortably, “Let's go to the next room I guess…”

“You sure? Are you okay?” Charlie asked worriedly.

She nodded with a slight smile and walked out of the scene.