The next door led into a, what seemed like, photographer's study. The explorers weren't sure, though, because of how dark the room was: the blinds of the only window were closed. Charlie walked over and opened them, the evening glare instantly pouring in through the glass.

The light fell onto a white sheet which was stuck to the wall, continuing on the floor. That was obviously the background for the photographer's photos. Before this stood a number of fairly old but seemingly fancy equipment like professional lighting and tripods. On the opposite side of the room was his desk with a matching chair and an ancient computer standing upon it, and before the desk stood another table with an equally old camera resting on it.

Overall, this room didn't have any drawers or anything interesting of the sort. But one thing did catch their eyes. It was a bulletin board covered in pictures which he obviously took. But it wasn't the pictures that had them interested. It was the newspaper cutouts.

The photos had nothing exciting on them. There were numbers and numbers of various people, none of which looked like the other which merely proved that he used to have a massive clientele.

The cutouts on the other hand were very intriguing. They were yellow and old now but were white headliners before.

“These two are dated way back in the late nineties!” Emily exclaimed, touching the two pieces of paper.

“'Local photographer won prestigious award' and ‘New art exhibition's special guest'…” Charlie read out loud, and then chuckled: “Seems like these are the only good news about him.”

And he was right. The other ones not only had creepy titles, but had some writing on them, like the photographer himself scribbled something onto the pages.

“This is horrifying… Look! He actually wrote ‘It was only 9' on an article called ‘10 people harassed by local photographer'!” Emily read, terrified.

“We can see, thank you!” Matthew called.

“Look, look, look!” Charlie took a page with the words ‘Local photographer seen on top of skyscraper' off the board and started reading: “'At least thirty people who were in Central Square at the time claim to have seen the previously beloved local photographer on the very top of the skyscraper, the ‘very top' being the roof. Some say he was jumping on the very edge and shouting something from up there, but no particular words could be heard. Others say he was standing quite still and, rumor has it, was preparing to jump off. But after a few moments he appeared…'”

“Go on!” Emily half-shouted, being so engrossed in the story as she was, “Read further!”

“There is no ‘further',” Charlie informed, showing her the page, “He wasn't very careful ripping it out.”

“Oh my…” she sighed, looking at the piece of paper.

“What?”

“The words ‘he was standing still and was preparing to jump off' are underlined.”

“Yeah, I noticed that.”

They both looked at each other, then turned back to see Matthew combing his hair with his hand. 

The two of them then turned back to the board. And as Charlie stuck the page back up, and moved his hand from article to article, he noticed that most of them had the same year written upon themselves – ‘2010'.

Each headline was more disturbing than the other. There was an article called ‘Local photographer wearing nothing but a bathrobe' and another one named ‘Local photographer seen naked out in public' dated one month apart. The most disturbing out of all of the ones dated ‘2010', though, was called ‘Our press set on fire by local photographer?'.

“Ooo, let's read this one,” Emily said, reaching for a page with ‘Psychotic behavior of local photographer explained' written in bold, black words on the very top.

“'Today we welcomed Dr. Grace Worth, PhD, into our cozy office and offered her a cup of tea so she could take us on a journey into the brain of our local photographer, Mr. Matthew Miller senior…',” she trailed off, her jaw almost dropping to the floor, and automatically looked up at Charlie.

He, in return, was already staring at Matthew. The auburn haired boy, on the other hand, was making it look like he wasn't bothered by this but was obviously doing it wrong. He was bending his neck with loud cracks and fiddling with the bottom of his shirt.

“IS THIS YOUR DAD?” Emily wondered very loudly, almost jumping on the spot.

Matthew said nothing. He didn't look at them: he had his head turned towards the white sheet stuck on the wall. Then he cleared his throat but still said nothing.

“So that's what that was all about…” Charlie muttered loudly enough for Matthew to look him up and down with worry.

“Is your dad still like this? Is he okay?” Emily questioned.

The boy, with his hand in his auburn hair, was quite for a moment, then he said dryly: “I don't know.”

“What do you mean you don't know?” Emily asked, amazed.

Matthew shook his head in silence.

“He dropped me off at a foster home when I was four and I haven't seen him since,” he stated in the same dry tone.

“Oh. I'm really sorry for that,” she said, and walked in his direction to give him a hug, “And I'm sorry for asking…”

“Well, I'm not!” Charlie exclaimed suddenly, “It's because of your dad that I ‘fell down from the banister'?!”

“I'm really sorry you did,” Matthew said, no regret seen on his face.

Charlie looked at him incredulously and then gave a glance to Emily who was standing near her weird boyfriend.

“Wait til Liz hears about this guy…” the ash brown haired boy murmured, shaking his head.

“Are you seriously going to tell her?” Matthew asked.

“What's wrong with telling Liz?” Emily wondered, pulling away from the embrace and taking a step back from him.

“Well… this is kind of personal, don't you think?” he replied.

“Well, yes, but she's a friend,” the blond girl gave a shrug.

“Don't get me wrong… But I don't want to distribute this information to other people.”

“Look who's using big words now!” Charlie noticed with a smile on his face.

“Come on, it's just one person…” Emily said, choosing to ignore her friend's remark.

“Yeah, and that person is a girl,” Matthew stated.

“What are you saying?” Emily stared at him, taking yet another step back.

“All girls are way too chatty, they can't seem to keep their mouth shut.”

“\textit{I'm} a girl.”

“My point exactly.”

“I'm going to ignore that because I know who your dad is and you're probably in shock…” she started, eyebrows raised and eyes closed.

“If you're saying I'm like my dad, then you're wrong. I'm \textit{nothing} like him,” Matthew cut in.

Emily kept silent, mouth slightly open, eyes narrowed. She turned to look at Charlie who, in return, was gazing crossly at Matthew.

“Alright, well, I'm still gonna tell Liz… cause she's my friend,” she informed.

“And I'm your \textit{boyfriend},” Matthew said, as if it was an implied fact and she ought to have memorized it by now.

“Yes, I \textit{know},” the blond girl replied in the same manner.

After a long silence with the casual exchange of dirty looks between the three of them, Emily stepped towards the door, still clutching the newspaper cutout.

“I think we should go to the next room…” she said quietly and opened the door, not even thinking of examining the rest of the articles, the ones dated ‘2011' and bearing such names as ‘Wife of local photographer gone missing', ‘Did the photographer's family really have a kid?' and ‘Local photographer disappeared' because she had more information than she ever needed.