The final door led into a very colorful room. There was a big desk with a much smaller chair on one side and a small bed with a red bedside table on the other. Between them – in the free space – stood a closet. And in the corner were two windows, the setting sun shining it’s pink-and-gold light onto a rug with lots of houses and roads drawn on it.

“So this was your room, huh?” Charlie asked, turning to a boy who looked like he was about to faint.

“Uh-huh,” Matthew answered weakly, touching the wall with his hand, as if holding onto it to support himself.

Emily, now visually mad at her boyfriend (Charlie could tell), made no sign of hearing him and went over to the desk to open its drawers.

“Wow, this is all extremely interesting,” she said with a yawn, flipping through all the ‘masterpieces’ that baby Matthew apparently drew.

Charlie opened up the closet and found himself looking at a bunch of baby clothes hanging from small hooks. On the only shelf at the very bottom of the construction stood a great wooden chest. Taking its lid off, Charlie wasn’t surprised to find a bunch of old and ragged toys inside.

“Nothing special in here either!” he called to Emily and they both headed to the bedside table while Matthew continued to stand completely still with a weak expression on his face.

“This room is boring,” Emily made a conclusion after seeing that there was nothing in the drawer near the bed.

“I guess we’ve seen all of the rooms now?” Charlie wondered, taking a quick look around Matthew’s old room.

“Yeah, I guess… And it’s only been three hours, it’s not even past curfew.”

“It isn’t anywhere near curfew. It’s like eight in the evening.”

“Well then… um… I guess that’s it? We just go home now?” Emily questioned.

Charlie nodded and both of them made a notion of going out the door when they noticed that Matthew wasn’t moving and was continuing to lean against the wall.

“What are you waiting for? An invitation?” Charlie asked, stopping right in front of the boy.

“I just… you know… I’d like to say my good-byes…” he said sadly.

“To the room?” Charlie raised an eyebrow.

Emily gave him a nudge with her elbow and jerked her head towards the door.

“We’ll wait for you outside. Don’t take long,” she informed, walked out the door with Charlie and closed it behind her.

\bigskip

Emily stood near Charlie, fiddling with the straps of her huge backpack. Her friend seemed to have noticed that and started:

“I’m sensing you want to talk to me about something?”

“Well, I’ve been actually meaning to ask you about that talk at the foot of the stairs… When you said something about Matthew,” she told him apprehensively.
“Yeah? What about it?”

“Did he say something to you? Something like what he said to me in the photographer’s room?”

“No, not exactly like that…” Charlie trailed off.

“Well what did he say?”

“It’s kinda hard to explain.”

“And did he make you slide down the banister and hurt yourself?” she asked worriedly.

“Kind of, yeah…” he answered uncertainly.

“How is… um…” she started uncomfortably, “your… erm, injured… area, by the way?”

“It’s okay…” he replied.

Dead silence had hung over them. The ash brown haired boy shuffled his feet on the landing’s carpet. And the blond girl patted the front and the back of her pants to dust off any dirt.

“Actually, it wasn’t because of the banister,” Charlie finally said.

“What was it then?”

“It was… well, how do I explain it?”

“Explain what?” a voice from behind them wondered loudly.

“We were… um, talking about… stuff and… I was, erm, trying to explain something to… Emily,” Charlie conjured the right words on the spot.

Matthew had walked out of his old room with a smile and was looking at them with some sort of pleasure. He nodded his head understandingly to Charlie’s words.

“Are we going home now?” the auburn haired boy questioned.

“Yep,” Emily nodded her head and led the way to climb down the staircase.

Once they reached the little hallway before the door, the three of them smiled at each other before going outside.

Emily reached the handle, turned it and pulled the door.

It didn’t open.

Her smile faded from her face as quickly as it appeared.

“What’s wrong?” Charlie asked, seeing the girl jiggle the handle in frustration.

“It… won’t… budge,” she replied, pulling at the door in between the words.

Charlie motioned his hand for his friend to step aside so he could try it himself. He jiggled the round stale door knob and pulled.

Nothing.

He stopped for a second and then tried to push it.

Nothing happened.

Charlie looked up at Emily with a worrisome expression on his face. Then they both looked at Matthew who was already pushing past both of them towards the door to try it himself.

He did everything they did.

The door didn’t move.

“This is bad,” Emily said in a panicky voice.

The three explorers looked at each other in horror. They can’t be stuck in here! Emily began pacing up and down the corridor.

“Oh!” Charlie exclaimed suddenly, “We can call somebody for help!”

And he made to reach for Emily’s backpack.

“Wait!” Emily said passionately, dropping her bag to the floor, and walked over to one of the windows in the hall, “We can open it and jump down! It’s only the first floor.”

“You’re right!” Charlie agreed, rushing to the window she was standing in front of.

They both grabbed the handle and pulled upwards.

Nothing.

“Well, it can’t go another way…” Emily said anxiously and then, jumping up, exclaimed: “Let’s try another one.”

Both of them, this time with Matthew, hurried to the window on the other side of the front door. They pulled upwards once again – all three at once – but nothing happened.

“What do we do now?” Matthew spoke in a stable but worried voice.

“Alright, um, let’s not panic over this… There are still other windows,” Emily answered firmly, “Let’s split up and check the whole downstairs and come back after.”

\bigskip

Standing in the small hallway with different kinds of anxious expressions spread about their faces, they couldn’t tell if it was dust or commotion in the air, as they had run from window to window and double-checked every single one with no result whatsoever. They were trapped.

“We can check the upstairs…” Emily started uncertainly.

“And jump from there?!” Charlie exclaimed, cutting her off.

“We can just check!”

“Alright, alright, don’t fight, you guys! Let’s go check,” Matthew piped in and then headed upstairs.

\bigskip

They had checked every single window and there wasn’t a back door: they now knew this house like the back of their own hands. But that didn’t help them in any way because they were stuck.

Charlie and Matthew were sitting on the first step at the bottom of the staircase, watching Emily pace up and down in front of them. Then, suddenly jumping, as she did from time to time when an idea came to her during the past half hour, she exclaimed:

“We can break a downstairs window and escape through it!”

“Firstly, what are we gonna break it with?” Matthew started.

“And secondly, even if we do, how are supposed to crawl through and not get hurt by the broken glass?!” Charlie finished for him.

“Isn’t getting hurt much more pleasing than being stuck in here forever?” Emily asked rhetorically.

“How are our parents going to react?!” Charlie questioned and then added: “Besides, we haven’t tried calling anybody for help!”

“Right!” the girl rushed to her backpack and pulled out her phone.

“Who am I supposed to call?” she asked, hesitating.

“I don’t know,” Charlie replied, “Try Liz.”

She obeyed, clicked on the contact in her phone called ‘Lizzie <3’ and reached her phone to her ear.

Nothing.

“What is the matter…” she said and, taking a look at her phone, added: “No bars...”

“No, it can’t be…” she muttered under her breath, starting to run around the floor and into rooms to stand up on furniture and try to get a signal, “No, no, no…”

“Try upstairs,” Matthew suggested once the blond girl came out of the kitchen, having stood on every piece of furniture she could.

She ran upstairs in frustration, holding her phone above her head and rushing into every room to stand on everything with Matthew and Charlie hurrying along with her.

No bars appeared.

“This is so weird, I mean…” she glanced up at the two boys, “I talked to Liz when we came here and everything was fine. And now there’s no signal…”

“Well then what are we going to do?” Matthew questioned.

They were slowly climbing down the staircase to sit on the bottom step again. And while Charlie and Matthew did sit down, Emily was restless and kept pacing up and down the small hallway.

She then stopped abruptly and looked carefully at the door.

After standing like that for a significant amount of time, she slowly walked over to her backpack, opened it and started to look into all of its pockets.

“What are you up to?” Charlie asked tiredly.

“Found it,” she mumbled and turned to the two boys with a hairpin in her hand.

“You brought a hairpin?!” Charlie rolled his eyes, standing up.

“We do need it now, don’t we?” she said, raising her eyebrows.

“Are you seriously saying you’re going to pick the lock with a hairpin?” Charlie questioned, walking over to the door, “Have you been watching too many movies?”

“We can at least try!” she said passionately, sticking the hairpin into the lock.

“I doubt it’ll do anything,” Charlie informed.

“Except get us even more stuck,” Matthew called from his seat at the bottom of the stairs.

Emily gave each of them a reproachful look and then turned her attention to the door. She jiggled the hairpin inside the keyhole calmly.

But it didn’t work, so she started wobbling it from one side of the too-big-for-it keyhole to the other with a lot of aggression. And then her fingers slipped off the thing metal wire that was the hairpin and it fell inside.

She froze in her spot, then looked up at the ceiling and sat down onto the floor, covering her face with her hands. Charlie, having stood there the whole time, got down beside her.

“Hey, we’ll figure something out,” he spoke comfortingly, putting his hand around her shoulders.

“I told you we shouldn’t go here!” she said, her voice muffled, “Now we’re trapped…”

“No, we’re not, we will find a way out, I promise.”

“Well, we have to hurry. It’s getting pretty late,” Matthew stated, looking at his watch and coming over to the spot where the two friends were sitting.

“Not helping,” Charlie said through gritted teeth, turning to Matthew.

“It’s okay,” she told him, uncovering her face, “We really do need to do something if we want to get out of here.”

“Honestly, I don’t know what else we could do,” Matthew sighed while the two friends stood up.

“We still haven’t tried breaking the glass of a window,” Charlie said hesitantly.

And while they searched for things that weren’t too heavy or too light to break the window with, Matthew shared the occasional thought that came to his mind. At the end, when they decided to go with the floor lamp that stood in the living room and had already picked it up, he formed the whole notion and shared:

“Hold on, so there are people living in this area, right?”

“Yeah, so? You already told us a few minutes ago,” Charlie said, holding onto the lamp’s hat.

“If they see somebody breaking the glass and climbing out, won’t they call the cops or something?”

Charlie and Emily let go of the lamp and looked at each other.

“What are you saying?” the girl questioned.

“I’m saying we could get in big trouble if they find out we broke into a house…”

“It’s an abandoned house,” Charlie corrected him.

“No, no, he has a point…” Emily said, “And I could get into more trouble because I broke that vanity mirror…”

“Then what are we supposed to do?” Charlie wondered in a cross tone.

“I don’t know…” Matthew replied.

“Well we don’t have any other ideas either so if you’ll be so kind as to help us get the hell out of here, it’d be great.”

“Look,” Matthew kept telling them, putting down the lamp onto the floor, “All I’m saying is we actually need to think about this carefully.”

“Look who’s constructing full sentences out of full words now!” Charlie exclaimed, clapping his hands.

“I know how to talk, what’s the problem?”

“So you don’t see anything wrong with the fact that we’re suddenly trapped in here?”

“I do, I just think there’s a better way of getting out. A way that doesn’t involve the cops coming after us, you know?”

Charlie took a deep breath. He merely wanted to get out of the creepy house but he surely didn’t want to have to deal with the police.

“Again, what are you suggesting we do?” Charlie repeated himself.

“We could stay the night and then maybe we will have signal in the morning…” he trailed off.

“ARE YOU CRAZY?” Emily shouted, “What are our parents supposed to think?!”

But before anybody could answer, she continued:

“Or maybe even better! We go break the upstairs windows and jump!”

“OR! OR!” she went on, not letting anyone cut her off, “We could chuck our phones from the top of the staircase…!”

“Wait!” Charlie exclaimed loudly, “Our phones!”

“What’s with our phones?” she asked, confused.

“We haven’t tried our phones!” he said, pointing at himself and at the auburn haired boy.

“You’re right!” she agreed with excitement, “Well, go on, try them!”

Both of the boys took out their phones and looked at the signal bars. Charlie immediately came over to the couch and stood up on it, while Matthew kept still.

“No bars,” Charlie concluded after returning from the staircase to which he rushed after he checked that there was no signal on the sofa.

“No bars either…” Matthew agreed.

“How can you tell? You haven’t tried…” Charlie started.

“If I don’t have any signal down here, I won’t have any signal up there,” he interrupted.

Both Charlie and Emily groaned in frustration. They can’t escape through the door or the windows because they’re locked. They can’t break a window because they’ll get caught trespassing. And they can’t call anybody because there is no signal.

They were both sitting on the couch now, having no idea of what to do. Emily opened her backpack and offered Charlie a mini-muffin which he took with a soft smile. Matthew kept pacing up and down the living room in which they used to want to break the window.

After a while he looked at his watch once more.

“It’s ten,” he informed, looking up.

“That’s our curfew,” Emily said bleakly, combing her hair with her hand.

“We’re really doomed, aren’t we?” Charlie sighed, “And literally. If we won’t find a way out and we’ll run out of food and water, it’s the end for us…”

Emily put her hand in her friend’s to try and comfort him. He stared at her with a soft look on his face and said with a chuckle:

“You weren’t paranoid after all.”

“Why are you saying it like that?”

“Like what?”

“Like we won’t get out and this is our good-bye?”

“Well, come on, it’s past curfew, and that means even if we do get out, we’ll still be dead because our parents will kill us.”

“I agree with the ‘our parents are going to kill us’ part, but we don’t have to necessarily give up… Maybe we just need a little rest…” she said uncomfortably.

“Are you saying we spend the night here?!” Charlie exclaimed.

She didn’t answer but tapped her foot nervously, looking up at Matthew.

“I mean, he has a point,” she sighed.

“No way! No way, no way, no way, no way,” Charlie shook his head furiously.

“What are we supposed to do?” Emily wondered, “We’re all tired here and we have no idea what else to do!”

“THINK!” he said passionately.

“We have been thinking for two hours straight, I think we deserve some rest,” Matthew piped in.

“I am not ‘resting’ for eight hours on this couch or on the upstairs bed.”

“Charlie, come on…” Emily kept trying to persuade him.

“No. It’d be better if I checked every window again instead of sitting my butt off, ‘resting’,” he snapped, stood up and left.

\bigskip

“Did you manage to escape?” Matthew chuckled.

Charlie had returned back to the living room after checking every window and the door, and even seeing if he had any bars.

“Very funny. Hilarious. Top comedy. Bravo!” he snapped and sat back onto the couch.

“We’ve decide to stay in the living room,” Emily said softly.

“I can see that you’ve waited for me in here, thank you.”

“No, I mean, stay the night in the living room…”

“Why?”

“None of us want to go upstairs.”

“Okay, fine.” he answered dryly.

“Matthew says that these armchairs are actually sleeper chairs so you and I are going to sleep on them and he’s going to sleep on the couch.”

“I don’t really care.”

Emily looked at him worriedly and sat down beside him, fishing out a sandwich that she prepared at home from her backpack. She offered it to him, knowing food usually calmed him down somehow. Or at least the food that she cooked.

He took the sandwich with a smile. She always knew how to cheer him up.

“Alright then, let’s go to sleep now…” he said uncertainly after having finished eating.

They both stood up, went over to the armchairs, found a strap underneath the seat and pulled at it, the armchair spreading into a bed with a squeak. Matthew was getting rid of all the back pillows on the couch, and once they were all done a dead silence had hung over them.

They each took their seats at their sleeping spaces and then awkwardly lay down, having no blankets whatsoever but having plenty of pillows and their clothes on.

The light didn’t have to be turned off either, as they had managed in the half-darkness, their eyes accustomed to it as they were.

They lay like that for a few moments and then all three of their voices were heard in the spacious living room:

“Good night,” they said and closed their eyes.