Charlie felt a warm sensation creeping through his whole body. But he didn’t wake up because he sensed it was part of his dream.

He dreamed of a cage and of a tall tree – basically, the usual. But there was a part that was most peculiar. He saw a dark figure getting closer to him and when it was at the point of being as close as ever, not leaving a centimeter between them, he saw who it was.

The photographer.

He was in his dream.

Charlie then felt small vibrations spreading through his upper body. And then a huge, big one like an earthquake.

And then a loud, hoarse whisper.

“Charlie!” the photographer called in the dream.

Then the boy felt a jerk and his dream ended. He opened his eyes and saw a real live figure above him. It was darker than ever in the living room. He couldn’t believe it wasn’t a dream because the person didn’t look anything like Emily or Matthew. He reached out to see if the person was, in fact, real. His hand felt the person’s face, their nose curve…

What else was Charlie supposed to do but to scream in horror? He felt his voice coming up from his throat and opened his mouth for it to come out but something warm came over it and muffled any sound.

“Listen, Charlie, we have to go,” the hoarse whisper continued.

Poor Charlie didn’t know what to do but keep screaming, the hand over his mouth converting any sound into a muffled ‘moo’.

“Please, please, listen to me,” the voice continued urgently, “We need to go right now. Matthew is setting this house on fire and you will burn alive if you don’t come with me.”

Charlie could feel his eyes growing to the size of ping-pong balls in the dark and stopped screaming abruptly.

The hand didn’t let go and his mouth was still captured in something soft and warm.

“Please,” the voice said again, “I know, it’s hard trusting me right now but I promise, I will never hurt you or Emily.”

Now that his eyesight was getting accommodated with its dark surroundings he could see the person in question more clearly but still didn’t understand what was going on. Charlie had so many questions and he definitely didn’t want to scream anymore. The person sensed this and slipped their hand off his face.

“Who are you?” was the first question he let out of his mouth.

“You don’t recognize me?” the person asked in a half-whisper.

Now the voice was even more familiar. And now that he was fully awake, Charlie remembered his dream – the shape of the person in front of him looked exactly like the figure of the photographer. His eyes were about to pop out of their sockets.

“ARE Y…” he started loudly but the hand went over his mouth once again.

“Yes, I am Mr. Brown and yes, it is surprising…” the voice replied, “But you have to remember that I am your neighbor and the fact that I’m the ‘mad photographer’ doesn’t change a thing. I still care about you deeply and I will never hurt you or Emily.”

Saying that Charlie was shocked would be an understatement because he was about to explode. Mr. Brown is the photographer?!

He instinctively turned his head to the armchair where Emily fell asleep.

She wasn’t there.

He jerked his head towards the sleeper chair and, seeing as he had a hand over his mouth, pointed towards it and a few angry muffled noises came from him.

“I promise, Charlie, Emily’s safe, but she won’t be if you keep sitting here because we’ll all burn alive,” Mr. Brown replied and let his hand slip off Charlie’s mouth.

“Why should I trust you? What if you’re making it all up about Matthew burning this place down?” the ash brown haired boy whispered furiously.

“So you haven’t noticed that his bed is empty and that it’s getting really warm down here?” his neighbor asked, “He started with the second floor so we have time, please come with me.”

“You dropped him off at a foster home when he was four!” Charlie said in a low whisper.

“And look what he came to be! Using his friends and girlfriend for his own well-being and committing arson!”

“Looks like he grew up to be his dad because you set the press on fire!”

“I promise I did no such thing!” he answered in frustration, “Frankly, I thought convincing you that the kid is up to no good would be much easier that Emily, yet here we are.”

Charlie pondered for a moment.

“Where is she?” he asked, still in a whisper.

“Near the kitchen.”

Charlie quickly stood up and followed his neighbor through the small hallway. They stopped at the corner between the entrance to the kitchen and the staircase. There was a dim light coming from an object – a flashlight – and it looked like Emily was holding it. She was facing the staircase’s part of the corner – the wall that was formed with the side of the stairs – and was shaking her hand from one side of it to the other.

“It’s us,” Mr. Brown called.

“You’re okay!” she exclaimed and was about to turn and hug Charlie, but his neighbor whispered:

“Keyhole!”

“Right,” she answered and kept shaking her hand.

“I have so many questions,” Charlie stated.

“Go ahead, we have time,” Mr. Brown said.

“Why are we whispering?” the boy asked in a low voice.

“If Matthew hears us, who knows what he’ll do!” Emily replied, but Mr. Brown patted her shoulder and she stopped talking abruptly.

“I think it’s time I keep guard, he could be done with the second floor at any moment,” Mr. Brown informed and went over to the bottom of the stairs, crouching down.

“What am I supposed to do?” Charlie asked.

“Ask questions and help Emily if she needs anything,” his neighbor answered.

“What is she doing, by the way?”

“Picking the basement lock.”

“THE…” he started loudly, but stopped and continued quietly: “Sorry… There’s a basement here?!”

“It’s been covered up with wallpaper all these years,” Emily answered.

“Wouldn’t it be easier if we picked the front door lock?”

“Emily told me you tried and dropped a pin inside. It’s not gonna work now,” Mr. Brown answered.

“How about the windows?”

“I don’t know what Matthew did, but they don’t open from the outside, neither do they open from the inside.”

“Wait, how did you get in?” Charlie questioned, arms crossed on his chest, and leaned towards Mr. Brown.

“I saw a ladder outside, leading to the second floor window and waited until you people were gone. And then, obviously, climbed in.”

“Well why don’t we climb through that window?”

“He dropped the ladder when he climbed in…” Emily said sadly and kept shaking her hand.

“I sure hope it wasn’t on purpose,” Charlie stated in a cross tone, glancing over at the man who was looking up onto the staircase.

“That’s the thing. It was,” Mr. Brown replied.

“WH…” he started loudly again, but calmed down: “What?! Why?!”

“So Matthew wouldn’t be able to get out, obviously.”

“What?!” Emily jumped up and for the first time turned to face Charlie.

She was holding a screwdriver and a thin metal wire contorted into an odd shape which was once a hairpin. She looked worriedly at Charlie’s neighbor who turned around and got closer to the two of them.

“Look, I know I probably made a mistake. Or maybe I bought us more time, who knows! But that is not important here. The important thing is that we get out in time,” he whispered.

“Well, who put the ladder there in the first place?” Charlie suddenly asked, not letting Emily or Mr. Brown get back to work.

“It was probably his friends. Closer to eight I saw some kids your age come over to the front door and windows, bringing ladders and rope and bags. They did something, and really fast, so I couldn’t even get a good look and then left one of the ladders at Matthew’s old room.”

“What do you mean ‘saw’?! Were you spying on us?” Charlie exclaimed, disturbed.

“Yes, and if it weren’t for me, you’d be asleep and dead. So get your arse over to the lock and pick it!” he snapped and turned over to stand guard.

“I don’t know how…” Charlie started but Emily gave him the screwdriver and led him to the door.

It was covered up really well, because while trying to escape and looking into every corner of the house, they haven’t noticed it at all. The middle part of the wallpaper was ripped off and on the floor: this was Mr. Brown and Emily trying to find the lock – and succeeding.

Emily went over to the corner and put the hairpin into the top of the lock and started jiggling it.

“Now is your cue!” she informed and, holding the flashlight with her hand now, rather than her armpit before, she continued: “The tip of the screwdriver has to go underneath the hairpin.”

He did as he was told and started jiggling it up and down. Then he suddenly stopped and, continuing to jiggle it further, asked:

“I still don’t get where could Matthew have gotten the equipment to start a fire. Did he run to the store and get some?”

“No, it was me…” Emily answered sadly, “I packed a box of matches. And he definitely took them because they’re not in my bag anymore… Oh, wait!”

“What?”

The girl bent down to the backpack which was standing in the corner and fished out some strange white pieces of cloth with strings tied to them.

“What are these?”

“My paranoia,” she answered, putting the mask on.

She then handed the two remaining ones to Charlie.

“They’ll make it easier to breathe, in the fire,” she clarified.

Charlie nodded, put one on and handed the last one to Mr. Brown. His neighbor looked at it, blinking a few times and then shoved Charlie’s hand out of the way.

“Oh, they never work,” he said.

“And still, put it on,” Emily replied, stopping mid-air before sticking the pin back into the keyhole.

“They’ll only make me hot!”

“If you just put it…”

“Look, just pick the lock faster so we can get out of here before it’ll get hard to breathe,” he snapped.

Emily nodded reluctantly and put the hairpin back into the keyhole. Charlie, though hesitating, put the white mask into his pants pocket and then turned his attention to the screwdriver.

But he then stopped to break the uncomfortable silence:

“Woah. Hold on a second! How did Mr. Brown know that Matthew was about to set us on fire?”

“I didn’t. I was supervising you from outside the house and then saw those kids coming, and then later everything had gone quite. But then I saw a person upstairs, and there was a lot of light coming from the room…” his neighbor replied, trailing off.

They were jiggling and shaking and moving the hairpin and the screwdriver for a lot of time now and they haven’t gotten anywhere.

“Let’s swap instruments,” Emily suggested.

Charlie nodded, handed her the screwdriver and got the hairpin in return. And once again, they began the procedure, but a minute hasn’t passed when Emily reached out her hand which was clutching the flashlight.

“Can you hold it for me?” she asked and let go of it.

Charlie wasn’t prepared and didn’t manage to catch it in time.

The thing is, that it was one of those gigantic, heavy, metal flashlights and it falling would be heard for kilometers. And since no one had managed to catch it, it fell onto the floorboards, causing the four of the people in the house to hear the loudest sound they’d ever heard in their entire lives.

How could the three of them, standing in the hallway, possibly know that Matthew heard it? Because after it fell down, everybody froze in their spot, waiting for something to happen. But a few seconds have passed and Matthew didn’t come, so Charlie bent down to pick it up.

And that’s when they heard footsteps from upstairs.

Mr. Brown instantly ducked down and mouthed ‘he’s coming’ so that the other two could duck down as well.

But it was too late. As they sat down onto the floor and pressed against the wall to make themselves invisible, they heard a voice above them say:
“I see you woke up! Something wrong?”

Charlie’s breath sped up and Emily could hear her heart pound against her rib cage. The boy slowly stood up, trying to cover Emily so her crazy boyfriend couldn’t see her. He then showed his face in between the bars of the banister, instantly seeing Matthew leaning over the railing.

“Well, it’s getting pretty hot in here, haven’t you noticed?” Charlie asked, trying to sound as confident as he could muster.

“The house is probably heating up. It happens in late spring,” Matthew answered, so obviously trying to sound like he wasn’t trying to burn this place down to ashes.

“Well, there’s also light coming from the ceiling… What’s that about?”

“Nothing, never mind… anyways, why are you and Emily up?” he questioned, not seeming to have noticed Mr. Brown down near the foot of the staircase.

Emily’s heart skipped a beat and she slowly got up, realizing this was probably the end for her and Charlie.

“Nothing, never mind,” Charlie answered in the same careless tone, “Why are you up?”

“Needed to use the bathroom,” he answered.

All three of them shared a glance.

Then, Matthew turned his head towards the front door and seemed to have noticed a person sitting there, pressed against the wall, because he turned his body in the direction.

“Who are you?” he called to Mr. Brown.

Charlie’s neighbor got up from the floor and looked his son straight in the eye.

“You don’t recognize your dad anymore, do you?” he said steadily.

The glance in Matthew’s eyes changed from soft and confused to furious. He ran down the rest of the stairs aggressively which made Emily and Charlie feel terrified for the well-being of Mr. Brown. They quickly rushed towards the foot of the staircase to prevent any kind of violence.

Matthew looked at them crossly and rolled his eyes but stopped abruptly on the first step.

“YOU! You left me in that wretched place when I was four!” he cried out, pointing at the man in question.

“Because I knew I couldn’t care for you…” his dad started but was cut off.

“And what happened to mom?!” his son continued.

“I…” the photographer started again.

“I AM ASKING YOU: WHAT HAPPENED TO MOM?!” Matthew roared.

“Please, calm down…” his dad started once more.

“CALM DOWN?!” Matthew shouted, “I will not calm down! You do realize that this is because of you?!”

“What? You committing arson?”

“The apple doesn’t fall far from the tree, does it?” Matthew shouted.

“I told you, I didn’t set that press on fire!!!”

“WHEN? Right before you put me in a foster home?!”

“Matthew, please, he’s right…” Emily piped in, “You don’t have to burn this house and everyone in it!”

“I do have to, because if I don’t, you’ll tell everyone at school what an embarrassment of a father I’ve got!” Matthew answered, giving her a dirty look.

“I promise, I won’t! Just please…” she started.

“How can I trust you?” Matthew questioned, interrupting her.

“Don’t you trust your girlfriend?”

He pondered for a moment and then answered with an aggressive ‘no’.

“Well,” Emily was desperately helpless, “Don’t you like me? Then you’ve got to trust me. That’s what love is…”

The auburn haired boy looked at her in confusion and then laughed hysterically, grabbing the railing to hold on to it. Emily and Charlie exchanged fearful looks as the thunder-like sounds rolled around the room, being accompanied by sizzling coming from the ceiling. When he finally stopped laughing, he leaned in closer to her and said:

“I never liked you. I never even tolerated you!”

Then he stood up straight again, leaving Emily open mouthed. He gave a little chuckle and added:

“Who would ever love such a pathetic creature of a human being?!”

Emily looked down at her hands, her fingers already fiddling with each other. Her heart was beating as fast as ever and her eyes were at the point of watering up when she heard Charlie step onto the first stair where Matthew was standing. She looked up, seeing her friend come closer and closer to Matthew and then finally breaking the silence.

“There are people who love her! I DO!” he shouted fiercely and his fist came swishing near Matthew’s head, though the guy ducked in time.

Charlie loving Emily? She thought she heard the wrong thing at the moment but realized it was what he actually said.

Matthew’s face grew scarier with rage and, without delay, he jumped to attack Charlie, when Mr. Brown came in front of his neighbor and took the blow to the face for him. Charlie was taken aback by this and stood frozen on the spot.

“Finish the job!” his neighbor cried while fighting his son.

The two friends as if woke up from a trance and quickly rushed to the basement door, ducking the blows that Matthew was sending with his fists.

They both took their instruments and started jabbing them inside the keyhole in frustration. 

It so happened that Emily put the screwdriver on top instead of the bottom of the hairpin and they tried getting it out when they heard a loud ‘CRASH’ followed by the crackling sounds of fire. Charlie straightened up and took a few steps back to get a glimpse of the living room’s ceiling collapsed, spreading the fire onto its furniture.

Emily urgently beckoned him towards her and suddenly turned the screwdriver. He got his hairpin into the keyhole and it only took a few jiggles when they heard the lock open.

They jumped up in surprise, Emily’s face lightening up. Then Charlie pushed the door and it opened up, revealing a wooden staircase leading into a dark room.

They kept hearing punches and kicks from the front door. And then Matthew’s voice:

“What was that?!”

Which was followed by even more punching and scrambling.

Then a part of the ceiling in the hallway, right in front of where Emily was standing, fell down, as if aiming for her, fire sizzling and crackling. The blond girl gave a little yelp, her face getting illuminated by the orange light, as Charlie pulled her back closer to the open door.

“Mr. Brown, are you coming?” she cried.

“I’m… holding… him…” his voice answered, kicking sounds heard in between the words, “Go! Now! I’ll catch up!”

The two friends were about to turn around and go down the stairs but stopped.

“How do we…” Charlie started shouting, the fire roaring, muting his voice.

“There’s a double door on the ceiling in the far corner of the room!” Mr. Brown cried, followed by a scream coming from Matthew.

The two friends went down the stairs, Emily dragging down her huge backpack which stood in the corner all this time.

“Drop it!” Charlie exclaimed loudly, seeing how the bag was slowing her down.

“What if we need it?” she shouted back at him.

She was almost at the bottom of the stairs when Charlie saw Matthew’s head appear in the basement doorway. He bore a psychotic expression on his face and started running down the steps. Charlie didn’t know what Matthew was prepared to do, but he didn’t want to take any chances. He grabbed Emily by her hand and hid her behind his back.

“Mr. Brown, are you okay?” the ash brown haired boy roared, trying to out-scream the fire, the flames of which were now dancing about the doorway.

Then his neighbor appeared, reaching his hand out for Matthew and grabbing him by the collar of his shirt just before he reached the two friends.

“Open the freaking door, will you!” he said and the father-son fight started all over again.

Emily and Charlie rushed to the furthest corner of the basement. Now that the fire was creeping about the room, burning the staircase with its touch, they didn’t need any flashlights to see that there was a double door on the very ceiling with a large drawers unit standing right underneath it. Emily stopped to open her backpack.

“Leave it here!” Charlie shouted.

“I’m taking stuff that we’ll need!” she cried.

“We won’t need anything if we burn to ashes! CLIMB UP!” he snapped at her, the fire roaring behind them and fighting noises being heard meekly.

He formed his hands into a double-fist for Emily to climb up and get to the top of the drawers unit. She had to bend down a little once she did so that she wouldn’t bump her head on the ceiling.

She reached her hands to the double doors above her, coughing from all the smoke, and pushed. They didn’t budge. 

Meanwhile Charlie was trying to get on top of the gigantic drawers unit and it wasn’t easy to do with all the toxic fumes and warmth in the once tranquil air. He finally figured it out: he put Emily’s backpack down and climbed on top, heaving himself onto the piece of furniture, Emily helping him get up.

“It won’t open!” she shouted.

“Together!” Charlie shouted back.

“One, two… three!”

They each pushed the wooden doors with their hands and shoulders. It started opening up and they pushed even with more effort still. The doors finally started listening and opened with a terrible screech, revealing the night sky with its moon.

“Mr. Brown! We opened them!” Charlie shouted, turning around to see the place ablaze and two figures way at the bottom of the drawers unit climbing onto each other and beating each other up.

“Climb out!” his neighbor called weakly but Charlie still heard him.

He helped Emily climb out onto the grass outside with a double-fist once again. She then reached her hand down for him.

They were covered in ashes and coughing horribly from all the smoke but they were alive! Emily embraced Charlie.

“You okay?” he asked.

“Yeah, you?” she replied.

“Yeah,” he said, breaking from the hug and, turning around to the open double doors, added: “All that’s left is…”

The basement was now almost completely covered in orange-and-yellow light of the terrible fire.

Charlie’s neighbor was nowhere to be seen.

“Mr. Brown!” they both called.

Nobody answered.

Charlie stuck his head as far as he could inside and called again.

No answer. Just the fire dancing around, roaring its terrifying song.

Charlie turned around to Emily and looked at her, his eyes searching for some kind of understanding in what he was about to ask her.

“Emily,” he started urgently, his mask covered in ashes, “Promise, promise me you’ll stay right here and won’t move no matter what!”

“What are you…” she started worriedly.

“Promise!” he shouted.

“I am not letting you go down there alone!” she shouted back.

“Please, please, stay here! I can’t afford to lose you…”

She looked deep into his eyes. Worry. She had seen this gaze before. It meant he won’t let go until you agree.

“Fine,” she answered, tears etched in her eyes.

He hugged her one more time, turned around and jumped down onto the top of the drawers unit. He then climbed down onto the backpack which still hasn’t caught fire and went around all the burning pieces and bits that were lying around the floor. He was looking for his neighbor, scanning the room with his eyes narrowed and coughing horribly.

A piece of the burning ceiling went flying right past him which he had to go around.

Then, suddenly, he saw a figure plastered on the floor. He rushed to it. It was a heap consisting of two people, both unconscious.

Matthew was on top and Mr. Brown – underneath him. Without hesitating, Charlie kicked Matthew aside with his foot as hard as he could and picked Mr. Brown up by the arm, wrapping it around his shoulder.

He wasn’t the easiest to carry, especially with the house being on fire and Charlie having to watch out for the burning patches of the floor.

He finally made his way to the drawers unit, only to see that Emily was waiting at the foot of it and not outside like he had asked.

“WHAT THE HELL?!” he shouted at her.

“You can’t do this alone!” she cried and wrapped Mr. Brown’s other arm around her shoulder.

They both made his neighbor’s legs go up onto the backpack with the fire creeping very close to it. Then Charlie climbed up onto the top of the drawers unit and with Emily pushing the photographer from the bottom and him pulling from the top, they managed to get him onto the piece of furniture. Then Emily climbed up as well and started pushing Mr. Brown out the double-doors while Charlie pulled at his arms, already standing on the outside.

They finally managed to pull him up and spread him on the grass, taking their masks off.

Emily breathed heavily, coughing a lot. Then she fished out a small water bottle from her pants pocket and offered it to Charlie.

“Where did you get this?” he asked, amazed and out of breath.

“When we were climbing up,” she started and coughed some more, “And I went to get some stuff out of the backpack.”

Charlie took the water, got some in his mouth and sprayed it across Mr. Brown’s face.

He didn’t wake up.

Charlie leaned in closer to his neighbor to listen to his heart. There was nothing to listen to. Just deafening silence.

He got up, his breath quivering.

“We have to call the ambulance!” Charlie said, his eyes watering up.

Emily fished out her phone from her other pants pocket.

“No signal again?” Charlie questioned, breathing heavily.

“One bar!” Emily informed, jumping up from her sitting position on the grass.

She walked over closer to Charlie, her breath shaking, her hands trembling.

“Hello?” was the next thing she said into the phone, her voice cracking, “Yes, please come. There’s been a fire…”