It was all a blur from there. Two ambulances arrived along with three firetrucks. The paramedics from the first ambulance instantly called the parents and then seated the two friends inside one of the vehicles and started checking their vitals while the paramedics from the second ambulance put Mr. Brown on a stretcher and started checking his vitals too.

In almost no time, Emily's and Charlie's parents were at the spot, hugging their children and answering questions from one of the firefighters.

The two friends were anxiously sitting on the built-in chairs inside the ambulance, waiting to be taken to the hospital, when a paramedic that had been with Mr. Brown came over to Charlie's parents.

“We're going to have to take him to the hospital, his condition is worse than we thought,” he informed.

The parents merely nodded, but Charlie stood up from his chair and ran over to the ambulance with Mr. Brown. Emily, though confused, went after him.

“Where are you going?” she asked.

The paramedics and their parents were now rushing after them to Mr. Brown.

“I need to be with him,” Charlie answered, his face tearstained.

“Then I'll come with you!”

“You need to go home and rest.”

“I'm not leaving you again!” she exclaimed, infuriated.

“Please don't make me worry about you too,” he answered sadly and got into the vehicle with his neighbor.

His parents looked questionably at the paramedics.

“Let him go; we're all headed to the same hospital,” one of them answered.

And Charlie, his parents and Mr. Brown were off, leaving Emily standing in front of the building where they were almost nearly killed.

\bigskip

Charlie was there. His parents were there. They were sitting in the doctor's office. There was a plate of cookies on the table right under Charlie's nose, but he wasn't hungry for them even though he hadn't eaten anything since Emily's sandwich before going to bed, and it was five in the morning now.

The doctor was looking at them with great despair in her eyes.

“I'm so sorry…” she said.

There was silence. The Rodriguez family was waiting for more information.

“He's at the state of biological death,” she informed sadly.

Charlie looked at her blankly and then felt a smile of hope etch onto his face.

“That…that's the one where he has a chance, where he's alive, right?” he asked.

The doctor shook her head slowly, her lips formed into a thin, almost invisible line.

Charlie felt his eyes burning from the hot tears that were just only forming.

“N…no, that's… that isn't right…” he repeated himself, “You can still save him, he's going to be okay, right? Right?”

When no answer but the grieving face of the doctor came, he heard his heart shatter into a million pieces. And, knowing he'd never get the pieces back together, he wanted to outshout the deafening sound of his breaking heart.

“No. No. He's fine. He's… he's going to be alright… He… I…” he started stuttering, gulping down the stream of tears running down his cheeks, “I want to see him. I have to see him. I've got to see him…”

“I am so sorry, but you can't…” the doctor replied in a kind but sad voice, “they're taking him to the morgue…”

“What? Why would you…” Charlie chuckled, his tears leaving stains on his heart he would never be able to get off, “Why would you take a perfectly healthy man to the morgue? That's ridiculous…”

The doctor shook her head, her expression letting Charlie know it was over.

“I am so sorry,” the doctor said again, because, Charlie could see, she really meant it, “We… we have to fill the… some paperwork and if you could wait outside…”

“Of course, I'm sure you did everything you could, thank you very much,” Charlie's mom spoke for the first time after looking at her son worriedly.

“No. No. No. I am not leaving until I see Mr. Brown, sitting in his bed… with… a… a smile and a…” Charlie started again.

He couldn't go on. But he also couldn't leave the doctor's office because he knew that once he did, he could never reverse it—any of it. He wouldn't be able to glue the pieces of his heart back together. He wouldn't be able to stitch the wounds in his shattered soul. He wouldn't be able to go on much longer. He couldn't. He just couldn't.

His mom and dad put their hands on his shoulders.

“We're sure you did everything you could…” his dad told the doctor kindly.

“Yes, thank you,” his mom added.

The doctor took her glasses off, dabbed her eyes with a handkerchief she took out of her pocket and gave them a kind of half-smile. That did not help Charlie's mood.

\bigskip

As soon as the doctor's door closed behind him and he was standing in the waiting room with his parents, without knowing it, he felt his body erupt. He let out a deafening scream of pain. Of the internal pain that comes with the loss of a close one, a loved one. He felt his face redden and his eyes ready to explode from the rush of tears. Eternal tears which will never ever end. He sat down onto a chair in the waiting room, bending in half and screaming, the scream so freezing that your soul would leave your body if you would ever hear it. Or feel it.

“I could've prevented our neighbor's death if I hadn't gone to the house…” he said quietly.

“Nobody knew this would happen. Don't blame yourself,” his dad spoke in a kind tone, getting down on a chair beside him.

“I know it hurts. It will hurt for a while, but never blame yourself for the way things turned out! Time heals, you know,” his mom added, seating herself next to her son.

Was it really true? Did time really heal? No, Charlie knew it didn't. It only made the pain more blunt, not as fragile as it was at first. But time doesn't truly heal. How can it? It is only time. He will forever be broken. Time will only try to find the missing pieces of his heart but will never be able to put them back together into the person he once was. His soul was now shattered for eternity; there was no turning back.

He suddenly stood up from his chair, remembering something he had almost forgotten—how could he? He then reached his hand into his pants pocket and sat back down, fishing out the mask, the mask his neighbor had touched.

His touch was covered in pocket lint. And guilt.

If only Charlie had \textit{forced} the mask onto Mr. Brown, he might still be alive. Injured, yes, but alive.

But he wasn't.

What was left was the mask.

And the guilt.

He covered his face with the mask and dug deep into his knees, sobbing harder and harder with every second. He wanted to scream again. The same deafening, soul-crushing scream he had screamed before. But he couldn't. Not anymore. He was so empty inside that he had no energy to scream anymore.