As the Rodriguez family neared their house, a silhouette of a short-haired girl was visible, standing in their front yard. Emily was biting her lip apprehensively.

“Hello, dear!” Charlie's mom said in a caring tone.

“Hello, Mrs. Rodriguez,” Emily replied, trying to smile.

“How did it go at the hospital?” she added, looking at Charlie.

“Erm…” Charlie started but couldn't go on and tilted his head to look down onto the grass he was standing on.

His mom put a hand on his shoulder to which he made a peculiar motion. She then looked at his dad.

“He's gone…” his dad said heavily.

“Oh,” Emily replied, her voice cracking.

Sensing that the kids wanted some time alone, Charlie's dad glanced at Charlie's mom and jerked his head towards the house.

“Emily, we're going to go inside and make toast and tea. You're invited in for breakfast,” Mrs. Rodriguez informed with a smile and went, along with Mr. Rodriguez, inside their home.

Once they had disappeared behind the front door, Charlie leaned on the fence that was surrounding their front yard. Emily stood beside him, lost for words.

“How are you?” she finally asked.

“I don't know.” Charlie cleared his throat, “I mean, I've known the man my whole life… But the last few years I, um, didn't talk to him as much… which apparently I now regret…”

“It's not your fault,” Emily tried comforting him.

“Okay, but these last few years he was trying to protect me the most.” Charlie looked into the distance. Emily leaned on the fence next to him, looking at the rising sun, which was sending pink and yellow waves of light around the sky.

“Like when he said I shouldn't try to impress you, he was, obviously, right.” Charlie sighed and inclined his head forward, resting it on his hands.

“You were trying to impress me?” Emily asked, astonished.

“Remember when I gave you a ride on my skateboard without my helmet? Just thought you liked Matthew for not wearing one.”

“I was genuinely concerned about you…” Emily stated, not believing how stupid he was if this was his way of "impressing" her.

“What else did Mr. Brown do?” she added to change the subject.

“Oh, when my parents and I had just moved here—I was about four or five—he came and brought a jar of cookies and a whole bag of old baby clothes,” Charlie chuckled softly, “My parents thought it was a 'weirdly sweet' gesture.”

Emily leaned forward to look at Charlie's face. He was on the verge of tears and his voice was cracking, but he looked like he was holding it in.

“Charlie, it's okay… You can cry,” she told him in a comforting tone.

He sighed deeply. Why was she like this all the time?

“I am trying to be strong,” he replied.

“For whom?” she furrowed her eyebrows.

“For you!” he snapped at her.

Charlie looked her right in the eyes for the first time after his love confession.

He couldn't stand Matthew breaking her heart in that house because he knew she liked him a lot. But he also hoped with all his heart—or, rather, what was left of it—that she would find a place for him in hers.

He loved her so much it hurt not to look at her, not to be in her presence, not to look at the sky together… He really did hope there could be a place for him in her soul. Maybe she loved him too?

Charlie was trying to figure out whether he should hug her or not, her ocean-blue eyes all red, when he noticed a figure in the distance.

“Who's that?” he wondered out loud.

He was pointing at a short man in a uniform, carrying a suitcase, who was nearing his house. Once the man had approached, he stopped right before the two friends.

“Is this where the Rodriguez family lives?” the man asked, checking a piece of paper.

Just at that moment, Charlie's parents appeared at the front door.

“You can come in for tea…” his mom began but trailed off.

“Hello..?” she added, spotting the man.

“Hello, ma'am, is this the Rodriguez residence?” he repeated his question.

“Yes, it is, why?” Charlie's dad answered.

“I need to talk to a 'Charlie Rodriguez',” the man read from his paper, “It's about Mr. Brown.”