The tea and toast was spread about the kitchen table in a welcoming way. Charlie's parents offered their guest a seat and he started:

“I'm very sorry for your loss.”

“Thank you,” Charlie answered, raising his eyebrows.

Did he have to sit through this and listen to this man say how sorry he is?

“We better get to the point,” the man continued and cleared his throat, “I'm Mr. Phillips and this is about Mr. Brown's will.”

“He has a will?” Charlie questioned.

“Yes. Yes, he does. And once again, let's get straight to the point,” Mr. Phillips repeated, “He left all his possessions to a 'Charlie Rodriguez'. Who here is Charlie Rodriguez?”

“Me…” the ash-brown haired boy replied uncertainly, being so astonished as he was.

Mr. Phillips looked him up and down and reached for his suitcase. He got a folder out.

“Now, there are some papers I'll need you to sign,” he informed, fishing out a stack of paper from the folder, “And then your parents should sign…”

He was interrupted by Emily clearing her throat loudly. Everyone glanced at her but she merely shook her head in reply.

“If you haven't yet…” Mr. Phillips started but was interrupted by Emily clearing her throat once again.

“Yes?” the man asked to which Emily shook her head for the second time, having said nothing.

Mr. Phillips continued but Emily couldn't understand what he was saying anymore. She heard him perfectly well but the words didn't make any sense, they were sort of muffled but at the same time too loud.

Her heart began to race against her rib cage even worse than it did back in that house when her life was in danger. She shook her head again, trying to shake it off.

Charlie glanced over at her with a worrisome look.

And suddenly it was hard to breathe. Emily felt like she would suffocate if she kept breathing through her nose as she normally did so she opened her mouth and started gasping for air loudly.

Everyone glanced over at her, but she didn't notice it because her eyes were filling up with tears so fast that her vision got blurry. She suddenly stood up from the chair she was sitting on and reached her shaking hand to her heart. It was pounding faster than ever and she couldn't control it.

She walked out into the hallway without saying a thing because she couldn't utter a word.

Emily heard voices that were barely there because of how loud her pounding heart was.

“Honey, are you okay?”

“What's wrong?!”

She heard them crowding over her as she sat down onto the hallway floor, sobbing louder and louder with every coming minute.

No amount of gasps of air was enough for her. She felt like this would never come to an end and that she'll spend her entire life in this state of suffocating.

She saw three blurry figures above her. They were all saying that it was going to be okay.

But that didn't help.

It only made it worse.

And she wailed even louder, not managing to form any words in her throat when another figure came into view. It looked like it was a boy with light brown skin, carrying a huge box.

“Get out, all of you. Come on now!” he snapped at the three blurry figures that were Mr. Phillips and Mr. and Mrs. Rodriguez.

They all murmured something, Emily not being able to catch their words, and left. The boy, though, sat down beside Emily with the box on his knees. He fished a green object out of it.

“Do you remember this?” Charlie's voice asked softly and Emily saw him showing her the rectangular object, “Here, you can take it if you want.”

She couldn't answer but kept gasping for air. She took the object in her shaking hands. It opened up and had pages inside with a lot of colorful shapes.

“This was the elephant that you drew for me in first grade, remember?” Charlie pointed at an odd blue shape.

Emily sobbed some more but nodded her head because she could even remember the exact crayon that she used to conjure this elephant up.

He flicked to a neon colored page and pointed at a pink diamond.

“What's this?” he questioned, looking at Emily.

She wiped her tears with the back of her hand, her heart beating fast, and moved the notebook closer to her eyes to see.

“A…” she started, trying to get more air with her mouth, “A… bubl… bubble… gum… r… wrap.”

“Yeah,” Emily could sense the smile in Charlie's voice, “We went to the amusement park that day and bought this gum. And then we liked it so much that we wanted more but couldn't find it anywhere except for that amusement park.”

He then got an oddly shaped object out of the box and handed it to Emily, taking the green notebook away.

“Know what this is?” he asked her, pointing at the silver object in the blond girl's hands.

She nodded, its shape becoming less blurry.

“It… It's… a… poe… pony,” she felt her voice slowly come back to her.

Emily took the deepest breath she ever took in her entire life and rested her face in her hands, dropping the silver pony.

“We made this pony together in third grade. It was really fun. We had no idea how to sew but it's still alive to this day,” Charlie chuckled.

Then Emily felt him slip something hard and rectangular onto her lap. She put her hands down onto the object and looked at it, her eyesight no longer blurry.

It was a framed photograph of a small, fair skinned and blond haired girl and a small ash-brown haired boy with light brown skin. They were both laughing about something, their faces decorated with glitter.

Emily looked at the two children in the picture, breathing as normally as she could. She looked over at her best friend. He was gazing at her intently, a soft and caring look etched on his face.

“Remember when we decorated the photo together…?” he started.

“I… I'm sorry…” she interrupted, her voice a whisper.

“For what?” he chuckled.

“I… I don't like you… that way,” Emily said, tears forming in her eyes again.

Charlie's eyes were no longer smiling. He opened his mouth slightly.

He heard his heart break for the second time – a loud, deafening noise that nobody but himself could hear. It was over. The world has crumbled completely.

How could he ever recover from all this pain, all this despair, all this misery? There was no hope, no love left.

Only darkness.

Oddly, he didn't want to cry. He was just… blank.

Blank like darkness itself.

“Oh,” he said, looked down and blinked a few times, Emily's words being stuck in his head, in his mind – forever.

“I'm sorry…” Emily whispered, putting the photo back into the box.

“It's okay,” Charlie smiled weakly, looking up at her.

“No, it's not…” she reached out to touch his hand.

“It is. It really is. I promise,” he scratched the back of his head with the hand Emily was about to touch, “Anyways, are you okay?”

She nodded. But she nodded not because she was okay, but because she understood that whatever happens they will always be friends. And that's what mattered the most.